---
title: "Prep Wetland Catchment and StreamCat N Data for Accumulation"
output: 
  html_document: 
    theme: yeti
---


# Code to prepare data for StreamCat processing

## Create combined N zonal stats for each RPU

*  Combines N from the 4 sources used in this analysis: cbnf, CMAQ, fertilizer, and manure

```{r, eval=F}
library(foreign)
library(dplyr)

zonal_path <- 'D:/WorkFolder/WetlandConnectivity/WetConnect_Apr2019/Wetlands_NLCD2011b/WetlandCat/Zonal/'

hydroregions <- read.csv(paste0(working_dir, 'hydro-regions.csv'))
names(hydroregions) <- c('Region', 'RPU', 'Hydro')

rpus <- as.character(hydroregions$RPU)
n_types <- c('cbnf_','CMAQ_','fert_','manure_')

for(i in 1:length(rpus)){
  print(rpus[i])
  for(k in 1:length(n_types)){
    print(n_types[k])
    tmp <- read.dbf(paste0(zonal_path, n_types[k], rpus[i],'.dbf'))[, c('Value','SUM','COUNT')]
    #Convert total kg 
    tmp$ha <- (tmp$COUNT * 900) * 0.0001  
    tmp$tmp <- (tmp$SUM / tmp$COUNT) * tmp$ha
    tmp <- tmp[, c('Value', 'tmp')]
    names(tmp) <- c('Value', n_types[k])
    if(k == 1){
      outdf <- tmp
    }else{
      outdf <- merge(outdf, tmp, by='Value', all=T)
      #Sum columns of N kg
      outdf$SUM <- rowSums(outdf[, 2:length(outdf)], na.rm = T)
      #Add dummy count column
      outdf$COUNT <- 1
      outdf <- outdf[, c('Value','COUNT','SUM')]
    }
  }
  write.dbf(outdf, file=paste0(zonal_path, 'TN_', rpus[i],'.dbf'))
}
```

## Calculate N applied to wetland catchment within each NHDPlus catchment 

```{r, eval=F}
library(foreign)
library(dplyr)

year='2011'

rds_path <- paste0('L:/Priv/CORFiles/Geospatial_Library_Projects/WetlandConnectivity/SpatialDataInputs/Wetlands_NLCD',year,'b/FinalTables/')
table_path = paste0(rds_path, 'WetlandTables/')
zonal_path <- 'D:/WorkFolder/WetlandConnectivity/WetConnect_Apr2019/Wetlands_NLCD2011b/WetlandCat/Zonal/'
nhd_path <- 'D:/GISData/NHDPlusV21'
n_zonal_path <- 'L:/Priv/CORFiles/Geospatial_Library_Projects/WetlandConnectivity/SpatialDataInputs/Wetlands_NLCD2011b/NitrogenModeling/Allocation_Accumulation/'
working_dir <- 'D:/WorkFolder/WetlandConnectivity/WetConnect_Apr2019/'

fullwetlands <- readRDS(paste0(rds_path, 'WetConnectMetrics_',year,'.rds'))
fullwetlands$Type_Full <- fullwetlands$Type
fullwetlands$Type <- ifelse(fullwetlands$Type=="Riparian", "Ripar", 
                            ifelse(fullwetlands$Type=="Overland", "NRSur",
                                   ifelse(fullwetlands$Type=='ShallowDeep' & fullwetlands$FreqClsPa=='VALUE_1',
                                          'NRSubPd', 'NRSubWd')))
fullwetlands$travel <- ifelse(fullwetlands$Type == 'NRSur', fullwetlands$MagOv, fullwetlands$MagSh)
fullwetlands$travel[fullwetlands$Type == 'Ripar'] <- 0
fullwetlands$travel <- fullwetlands$travel + 1
fullwetlands <- subset(fullwetlands, select = c(WetId,COMID,Type,travel))

rpucomid <- read.csv('L:/Priv/CORFiles/Geospatial_Library_Projects/StreamCat/COMID_HydroRegion_RPU.csv')[c('COMID','RPU')]

hydroregions <- read.csv(paste0(working_dir, 'hydro-regions.csv'))
names(hydroregions) <- c('Region', 'RPU', 'Hydro')

hydro.rgns <- c("01","02","03S","03N","03W","04","05","06","07","08","09","10L","10U","11","12","13","14","15","16","17","18")
rgns <- c("NE","MA","SA","SA","SA","GL","MS","MS","MS","MS","SR","MS","MS","MS","TX","RG","CO","CO","GB","PN","CA")

for(i in 1:length(hydro.rgns)){
  print(hydro.rgns[i])
  
  cats = read.dbf(paste0(nhd_path,"/NHDPlus",rgns[i],"/NHDPlus",hydro.rgns[i],"/NHDPlusCatchment/Catchment.dbf"))[, c('GRIDCODE','FEATUREID')]
  
  rpus <- hydroregions$RPU[hydroregions$Hydro %in% hydro.rgns[i]]
  
  #Combine zonal DBFs from RPUs for each VPU
  for(j in 1:length(rpus)){
    tmp <- read.dbf(paste0(zonal_path, 'TN_', rpus[j],'.dbf'))[, c('Value','SUM','COUNT')]
    if(j == 1){
      zonal <- tmp
    }else{
      zonal <- rbind(zonal, tmp)
    }
  }
  
  #Combine wetland basin area file from RPUs for each VPU
  #Any of the final tables could be used. Simply need COMID-WETLAND ID connection
  for(j in 1:length(rpus)){
    tmp <- read.csv(paste0(table_path, 'BasinAreaSqKm_', rpus[j], '.csv'))[, c('WET_ID','COMID','CatAreaSqKm','WetlandAreaSqKm')]
    tmp <- merge(tmp, rpucomid, by='COMID')
    tmp <- tmp[tmp$RPU %in% rpus[j], ]
    if(j == 1){
      ids <- tmp
    }else{
      ids <- rbind(ids, tmp)
    }
  }
  
  #Merge tables
  zonal <- merge(zonal, ids, by.x='Value', by.y='WET_ID')
  names(zonal)[1] <- 'VALUE'
  
  #Get wetland travel times and merge with zonal
  tmp <- fullwetlands[fullwetlands$COMID %in% zonal$COMID, ]
  tmp <- subset(tmp, select = -COMID)
  
  zonal <- merge(zonal, tmp, by.x='VALUE', by.y='WetId')
  
  zonal$ha <- (zonal$COUNT * 900) * 0.0001  
  zonal$kg <- (zonal$SUM / zonal$COUNT) * zonal$ha
  zonal$newsum <- zonal$kg / (zonal$WetlandAreaSqKm * 100)
  zonal$newsum2 <- zonal$kg / (zonal$travel)
  zonal$newsum3 <- zonal$kg / (zonal$WetlandAreaSqKm * 100) / (zonal$travel)
  
  zonal0 <- zonal %>% group_by(Type, COMID) %>% summarize(SUM=sum(kg),
                                                          COUNT=sum(COUNT),
                                                          AREA=max(CatAreaSqKm)*1e6)
  
  zonal1 <- zonal %>% group_by(Type, COMID) %>% summarize(SUM=sum(newsum),
                                                          COUNT=sum(COUNT),
                                                          AREA=max(CatAreaSqKm)*1e6)
  
  zonal2 <- zonal %>% group_by(Type, COMID) %>% summarize(SUM=sum(newsum2),
                                                          COUNT=sum(COUNT),
                                                          AREA=max(CatAreaSqKm)*1e6)
  
  zonal3 <- zonal %>% group_by(Type, COMID) %>% summarize(SUM=sum(newsum3),
                                                          COUNT=sum(COUNT),
                                                          AREA=max(CatAreaSqKm)*1e6)
  
  
  zonal0 <- merge(zonal0, cats, by.x='COMID', by.y='FEATUREID')
  names(zonal0)[length(zonal0)] <- 'VALUE'
  zonal0 <- zonal0[, c('VALUE','COUNT','AREA','SUM','Type')]
  zonal0 <- zonal0[!is.na(zonal0$SUM), ]
  
  zonal1 <- merge(zonal1, cats, by.x='COMID', by.y='FEATUREID')
  names(zonal1)[length(zonal1)] <- 'VALUE'
  zonal1 <- zonal1[, c('VALUE','COUNT','AREA','SUM','Type')]
  zonal1 <- zonal1[!is.na(zonal1$SUM), ]
  
  zonal2 <- merge(zonal2, cats, by.x='COMID', by.y='FEATUREID')
  names(zonal2)[length(zonal2)] <- 'VALUE'
  zonal2 <- zonal2[, c('VALUE','COUNT','AREA','SUM','Type')]
  zonal2 <- zonal2[!is.na(zonal2$SUM), ]
  
  zonal3 <- merge(zonal3, cats, by.x='COMID', by.y='FEATUREID')
  names(zonal3)[length(zonal3)] <- 'VALUE'
  zonal3 <- zonal3[, c('VALUE','COUNT','AREA','SUM','Type')]
  zonal3 <- zonal3[!is.na(zonal3$SUM), ]
  
  write.dbf(zonal0, file=paste0(n_zonal_path, 'DBF_stash/', 'TN_TotalKg_', hydro.rgns[i], '.dbf'))
  write.dbf(zonal1, file=paste0(n_zonal_path, 'DBF_stash/', 'TN_ByWtArea_', hydro.rgns[i], '.dbf'))
  write.dbf(zonal2, file=paste0(n_zonal_path, 'DBF_stash/', 'TN_ByTravelTime_', hydro.rgns[i], '.dbf'))
  write.dbf(zonal3, file=paste0(n_zonal_path, 'DBF_stash/', 'TN_ByAreaTime_', hydro.rgns[i], '.dbf'))
}
```

## Calculate N applied to wetland catchment within each NHDPlus catchment by **wetlands type**

```{r, eval=F}
library(foreign)
library(dplyr)

year='2011'

rds_path <- paste0('L:/Priv/CORFiles/Geospatial_Library_Projects/WetlandConnectivity/SpatialDataInputs/Wetlands_NLCD',year,'b/FinalTables/')
table_path = paste0(rds_path, 'WetlandTables/')
zonal_path <- 'D:/WorkFolder/WetlandConnectivity/WetConnect_Apr2019/Wetlands_NLCD2011b/WetlandCat/Zonal/'
nhd_path <- 'D:/GISData/NHDPlusV21'
n_zonal_path <- 'L:/Priv/CORFiles/Geospatial_Library_Projects/WetlandConnectivity/SpatialDataInputs/Wetlands_NLCD2011b/NitrogenModeling/Allocation_Accumulation/'
working_dir <- 'D:/WorkFolder/WetlandConnectivity/WetConnect_Apr2019/'

fullwetlands <- readRDS(paste0(rds_path, 'WetConnectMetrics_',year,'.rds'))
fullwetlands$Type_Full <- fullwetlands$Type
fullwetlands$Type <- ifelse(fullwetlands$Type=="Riparian", "Ripar", 
                            ifelse(fullwetlands$Type=="Overland", "NRSur",
                                   ifelse(fullwetlands$Type=='ShallowDeep' & fullwetlands$FreqClsPa=='VALUE_1',
                                          'NRSubPd', 'NRSubWd')))
fullwetlands$travel <- ifelse(fullwetlands$Type == 'NRSur', fullwetlands$MagOv, fullwetlands$MagSh)
fullwetlands$travel[fullwetlands$Type == 'Ripar'] <- 0
fullwetlands$travel <- fullwetlands$travel + 1
fullwetlands <- subset(fullwetlands, select = c(WetId,COMID,Type,travel))

rpucomid <- read.csv('L:/Priv/CORFiles/Geospatial_Library_Projects/StreamCat/COMID_HydroRegion_RPU.csv')[c('COMID','RPU')]

hydroregions <- read.csv(paste0(working_dir, 'hydro-regions.csv'))
names(hydroregions) <- c('Region', 'RPU', 'Hydro')

hydro.rgns <- c("01","02","03S","03N","03W","04","05","06","07","08","09","10L","10U","11","12","13","14","15","16","17","18")
rgns <- c("NE","MA","SA","SA","SA","GL","MS","MS","MS","MS","SR","MS","MS","MS","TX","RG","CO","CO","GB","PN","CA")


for(i in 1:length(hydro.rgns)){
  print(hydro.rgns[i])
  
  cats = read.dbf(paste0(nhd_path,"/NHDPlus",rgns[i],"/NHDPlus",hydro.rgns[i],"/NHDPlusCatchment/Catchment.dbf"))[, c('GRIDCODE','FEATUREID')]
  
  rpus <- hydroregions$RPU[hydroregions$Hydro %in% hydro.rgns[i]]
  
  #Combine zonal DBFs from RPUs for each VPU
  for(j in 1:length(rpus)){
    tmp <- read.dbf(paste0(zonal_path, 'TN_', rpus[j],'.dbf'))[, c('Value','SUM','COUNT')]
    if(j == 1){
      zonal <- tmp
    }else{
      zonal <- rbind(zonal, tmp)
    }
  }
  
  #Combine wetland basin area file from RPUs for each VPU
  #Any of the final tables could be used. Simply need COMID-WETLAND ID connection
  for(j in 1:length(rpus)){
    tmp <- read.csv(paste0(table_path, 'BasinAreaSqKm_', rpus[j], '.csv'))[, c('WET_ID','COMID','CatAreaSqKm','WetlandAreaSqKm')]
    tmp <- merge(tmp, rpucomid, by='COMID')
    tmp <- tmp[tmp$RPU %in% rpus[j], ]
    if(j == 1){
      ids <- tmp
    }else{
      ids <- rbind(ids, tmp)
    }
  }
  
  #Merge tables
  zonal <- merge(zonal, ids, by.x='Value', by.y='WET_ID')
  names(zonal)[1] <- 'VALUE'
  
  #Get wetland travel times and merge with zonal
  tmp <- fullwetlands[fullwetlands$COMID %in% zonal$COMID, ]
  tmp <- subset(tmp, select = -COMID)
  
  zonal <- merge(zonal, tmp, by.x='VALUE', by.y='WetId')
  
  zonal$ha <- (zonal$COUNT * 900) * 0.0001  
  zonal$kg <- (zonal$SUM / zonal$COUNT) * zonal$ha
  zonal$newsum <- zonal$kg / (zonal$WetlandAreaSqKm * 100)
  zonal$newsum2 <- zonal$kg / (zonal$travel)
  zonal$newsum3 <- zonal$kg / (zonal$WetlandAreaSqKm * 100) / (zonal$travel)
  
  zonal0 <- zonal %>% group_by(Type, COMID) %>% summarize(SUM=sum(kg),
                                                          COUNT=sum(COUNT),
                                                          AREA=max(CatAreaSqKm)*1e6)
  
  zonal1 <- zonal %>% group_by(Type, COMID) %>% summarize(SUM=sum(newsum),
                                                          COUNT=sum(COUNT),
                                                          AREA=max(CatAreaSqKm)*1e6)
  
  zonal2 <- zonal %>% group_by(Type, COMID) %>% summarize(SUM=sum(newsum2),
                                                          COUNT=sum(COUNT),
                                                          AREA=max(CatAreaSqKm)*1e6)
  
  zonal3 <- zonal %>% group_by(Type, COMID) %>% summarize(SUM=sum(newsum3),
                                                          COUNT=sum(COUNT),
                                                          AREA=max(CatAreaSqKm)*1e6)
  
  
  zonal0 <- merge(zonal0, cats, by.x='COMID', by.y='FEATUREID')
  names(zonal0)[length(zonal0)] <- 'VALUE'
  zonal0 <- zonal0[, c('VALUE','COUNT','AREA','SUM','Type')]
  
  zonal1 <- merge(zonal1, cats, by.x='COMID', by.y='FEATUREID')
  names(zonal1)[length(zonal1)] <- 'VALUE'
  zonal1 <- zonal1[, c('VALUE','COUNT','AREA','SUM','Type')]
  
  zonal2 <- merge(zonal2, cats, by.x='COMID', by.y='FEATUREID')
  names(zonal2)[length(zonal2)] <- 'VALUE'
  zonal2 <- zonal2[, c('VALUE','COUNT','AREA','SUM','Type')]
  
  zonal3 <- merge(zonal3, cats, by.x='COMID', by.y='FEATUREID')
  names(zonal3)[length(zonal3)] <- 'VALUE'
  zonal3 <- zonal3[, c('VALUE','COUNT','AREA','SUM','Type')]
  
  wet_types <- unique(na.omit(zonal$Type))
  
  for(j in 1:length(wet_types)){
    z0 <- na.omit(zonal0[zonal0$Type == wet_types[j], ])
    z1 <- na.omit(zonal1[zonal1$Type == wet_types[j], ])
    z2 <- na.omit(zonal2[zonal2$Type == wet_types[j], ])
    z3 <- na.omit(zonal3[zonal3$Type == wet_types[j], ])
    write.dbf(z0, file=paste0(n_zonal_path, 'DBF_stash/', 'TN_TotalKg_', wet_types[j], '_', hydro.rgns[i], '.dbf'))
    write.dbf(z1, file=paste0(n_zonal_path, 'DBF_stash/', 'TN_ByWtArea_', wet_types[j], '_', hydro.rgns[i], '.dbf'))
    write.dbf(z2, file=paste0(n_zonal_path, 'DBF_stash/', 'TN_ByTravelTime_', wet_types[j], '_', hydro.rgns[i], '.dbf'))
    write.dbf(z3, file=paste0(n_zonal_path, 'DBF_stash/', 'TN_ByAreaTime_', wet_types[j], '_', hydro.rgns[i], '.dbf'))
  }
}
```

## Calculate wetland area by **wetlands type** for StreamCat accumulation

```{r, eval=F}
library(foreign)
library(dplyr)

year='2011'

rds_path <- paste0('L:/Priv/CORFiles/Geospatial_Library_Projects/WetlandConnectivity/SpatialDataInputs/Wetlands_NLCD',year,'b/FinalTables/')
table_path = paste0(rds_path, 'WetlandTables/')
zonal_path <- 'D:/WorkFolder/WetlandConnectivity/WetConnect_Apr2019/Wetlands_NLCD2011b/WetlandCat/Zonal/'
nhd_path <- 'D:/GISData/NHDPlusV21'
n_zonal_path <- 'L:/Priv/CORFiles/Geospatial_Library_Projects/WetlandConnectivity/SpatialDataInputs/Wetlands_NLCD2011b/NitrogenModeling/Allocation_Accumulation/'
working_dir <- 'D:/WorkFolder/WetlandConnectivity/WetConnect_Apr2019/'

fullwetlands <- readRDS(paste0(rds_path, 'WetConnectMetrics_',year,'.rds'))
fullwetlands$Type_Full <- fullwetlands$Type
fullwetlands$Type <- ifelse(fullwetlands$Type=="Riparian", "Ripar", 
                            ifelse(fullwetlands$Type=="Overland", "NRSur",
                                   ifelse(fullwetlands$Type=='ShallowDeep' & fullwetlands$FreqClsPa=='VALUE_1',
                                          'NRSubPd', 'NRSubWd')))
fullwetlands$travel <- ifelse(fullwetlands$Type == 'NRSur', fullwetlands$MagOv, fullwetlands$MagSh)
fullwetlands$travel[fullwetlands$Type == 'Ripar'] <- 0
fullwetlands$travel <- fullwetlands$travel + 1
fullwetlands <- subset(fullwetlands, select = c(WetId,COMID,Type,travel))
fullwetlands$wetid_comid <- paste0(fullwetlands$WetId, '_', fullwetlands$COMID)

rpucomid <- read.csv('L:/Priv/CORFiles/Geospatial_Library_Projects/StreamCat/COMID_HydroRegion_RPU.csv')[c('COMID','RPU')]

hydroregions <- read.csv(paste0(working_dir, 'hydro-regions.csv'))
names(hydroregions) <- c('Region', 'RPU', 'Hydro')

hydro.rgns <- c("01","02","03S","03N","03W","04","05","06","07","08","09","10L","10U","11","12","13","14","15","16","17","18")
rgns <- c("NE","MA","SA","SA","SA","GL","MS","MS","MS","MS","SR","MS","MS","MS","TX","RG","CO","CO","GB","PN","CA")

for(i in 1:length(hydro.rgns)){
  print(hydro.rgns[i])
  
  cats = read.dbf(paste0(nhd_path,"/NHDPlus",rgns[i],"/NHDPlus",hydro.rgns[i],"/NHDPlusCatchment/Catchment.dbf"))[, c('GRIDCODE','FEATUREID')]
  
  rpus <- hydroregions$RPU[hydroregions$Hydro %in% hydro.rgns[i]]
  
  #Combine wetland basin area file from RPUs for each VPU
  #Any of the final tables could be used. Simply need COMID-WETLAND ID connection
  for(j in 1:length(rpus)){
    tmp <- read.csv(paste0(table_path, 'BasinAreaSqKm_', rpus[j], '.csv'))[, c('WET_ID','COMID','CatAreaSqKm','WetlandAreaSqKm')]
    tmp <- merge(tmp, rpucomid, by='COMID')
    tmp <- tmp[tmp$RPU %in% rpus[j], ]
    if(j == 1){
      zonal <- tmp
    }else{
      zonal <- rbind(zonal, tmp)
    }
  }
  
  zonal <- zonal[!duplicated(zonal), ]
  zonal$wetid_comid <- paste0(zonal$WET_ID, '_', zonal$COMID)
  zonal <- subset(zonal, select=-COMID)
  
  zonal <- merge(zonal, fullwetlands, by='wetid_comid')

  zonal$SUM <- zonal$WetlandAreaSqKm * 100
  zonal$COUNT <- (zonal$WetlandAreaSqKm * 1e6) / 900

  zonal0 <- zonal %>% group_by(Type, COMID) %>% summarize(SUM=sum(SUM),
                                                          COUNT=sum(COUNT),
                                                          AREA=max(CatAreaSqKm)*1e6)
  
  zonal0 <- merge(zonal0, cats, by.x='COMID', by.y='FEATUREID')
  names(zonal0)[length(zonal0)] <- 'VALUE'
  zonal0 <- zonal0[, c('VALUE','COUNT','AREA','SUM','Type')]
  
  wet_types <- unique(na.omit(zonal$Type))
  
  for(j in 1:length(wet_types)){
    z0 <- na.omit(zonal0[zonal0$Type == wet_types[j], ])
    write.dbf(z0, file=paste0(n_zonal_path, 'DBF_stash/', 'WtAreasByType_', wet_types[j], '_', hydro.rgns[i], '.dbf'))
  }
}
```

# Aggregate tables to calculate mean number of downslope wetlands

```{r, eval=F}
library(foreign)
library(dplyr)

year='2011'

table_path = paste0('L:/Priv/CORFiles/Geospatial_Library_Projects/WetlandConnectivity/SpatialDataInputs/Wetlands_NLCD',year,'b/FinalTables/WetlandTables/')
accum_path <- 'D:/WorkFolder/WetlandConnectivity/WetConnect_Apr2019/Wetlands_NLCD2011b/WetlandPath/Accumulation/'
nhd_path <- 'D:/GISData/NHDPlusV21'
n_zonal_path <- 'L:/Priv/CORFiles/Geospatial_Library_Projects/WetlandConnectivity/SpatialDataInputs/Wetlands_NLCD2011b/NitrogenModeling/Allocation_Accumulation/'
working_dir <- 'D:/WorkFolder/WetlandConnectivity/WetConnect_Apr2019/'

hydroregions <- read.csv(paste0(working_dir, 'hydro-regions.csv'))
names(hydroregions) <- c('Region', 'RPU', 'Hydro')

hydro.rgns <- c("01","02","03S","03N","03W","04","05","06","07","08","09","10L","10U","11","12","13","14","15","16","17","18")
rgns <- c("NE","MA","SA","SA","SA","GL","MS","MS","MS","MS","SR","MS","MS","MS","TX","RG","CO","CO","GB","PN","CA")

for(i in 1:length(hydro.rgns)){
  print(hydro.rgns[i])
  
  cats = read.dbf(paste0(nhd_path,"/NHDPlus",rgns[i],"/NHDPlus",hydro.rgns[i],"/NHDPlusCatchment/Catchment.dbf"))[, c('GRIDCODE','FEATUREID','AreaSqKM')]
  
  rpus <- hydroregions$RPU[hydroregions$Hydro %in% hydro.rgns[i]]
  
  #Combine zonal DBFs from RPUs for each VPU
  for(j in 1:length(rpus)){
    tmp <- read.csv(paste0(accum_path, 'DwnSlpWetlands_SUM_', rpus[j],'.csv'))#[, c('Value','SUM','COUNT')]
    if(j == 1){
      zonal <- tmp
    }else{
      zonal <- rbind(zonal, tmp)
    }
  }
  
  names(zonal) <- c('VALUE','SUM')
  
  #Combine wetland basin area file from RPUs for each VPU
  #Any of the final tables could be used. Simply need COMID-WETLAND ID connection
  for(j in 1:length(rpus)){
    tmp <- read.csv(paste0(table_path, 'BasinAreaSqKm_', rpus[j], '.csv'))[, c('WET_ID','PATHID','COMID','Riparian','WetlandAreaSqKm')]
    if(j == 1){
      ids <- tmp
    }else{
      ids <- rbind(ids, tmp)
    }
  }
  
  #Merge tabless
  zonal <- merge(zonal, ids, by.x='VALUE', by.y='PATHID', all.y=T)
  #Adjust riparian and no-path wetlands to be 0
  zonal$SUM[zonal$SUM == 1 & zonal$Riparian == 1] <- 0
  zonal$SUM[is.na(zonal$SUM) & zonal$Riparian == 1] <- 0
  
  zonal2 <- zonal[zonal$SUM > 0, ]
  
  zonal <- zonal %>% group_by(COMID) %>% summarize(SUM=sum(SUM),
                                                   COUNT=n(),
                                                   WetlandAreaSqKm = sum(WetlandAreaSqKm))
  zonal2 <- zonal2 %>% group_by(COMID) %>% summarize(SUM=sum(SUM),
                                                   COUNT=n(),
                                                   WetlandAreaSqKm = sum(WetlandAreaSqKm))
  
  zonal <- merge(zonal, cats, by.x='COMID', by.y='FEATUREID', all.y=T)
  zonal <- zonal[, c('GRIDCODE','COUNT','AreaSqKM','SUM')]
  names(zonal) <- c('VALUE','COUNT','AREA','SUM')
  zonal$AREA <- zonal$AREA * 1e6
  zonal[is.na(zonal)] <- 0
  
  zonal2 <- merge(zonal2, cats, by.x='COMID', by.y='FEATUREID', all.y=T)
  zonal2 <- zonal2[, c('GRIDCODE','COUNT','AreaSqKM','SUM')]
  names(zonal2) <- c('VALUE','COUNT','AREA','SUM')
  zonal2$AREA <- zonal2$AREA * 1e6
  zonal2[is.na(zonal2)] <- 0
  
  write.dbf(zonal, file=paste0(n_zonal_path, 'DBF_stash/', 'CountDwnSlpWetlands_', hydro.rgns[i], '.dbf'))
  write.dbf(zonal2, file=paste0(n_zonal_path, 'DBF_stash/', 'CountDwnSlpWetlandsNR_', hydro.rgns[i], '.dbf'))
}
```

# Aggregating StreamCat output into long files

## Combine StreamCat wetland N accumulations to single (2.6 million records) files 

```{r, eval=F}
year='2011'

working_dir <- 'D:/WorkFolder/WetlandConnectivity/WetConnect_Apr2019/'
nmodel_dir <- paste0(working_dir,'nitrogen-modeling/')
accum_dir <- 'L:/Priv/CORFiles/Geospatial_Library_Projects/WetlandConnectivity/SpatialDataInputs/Wetlands_NLCD2011b/NitrogenModeling/Allocation_Accumulation/'

TNs <- c('TN_TotalKg_','TN_ByAreaTime_','TN_ByTravelTime_','TN_ByWtArea_')
hydro.rgns <- c("01","02","03S","03N","03W","04","05","06","07","08","09","10L","10U","11","12","13","14","15","16","17","18")

for(i in 1:length(TNs)){
  print(TNs[i])
  for(k in 1:length(hydro.rgns)){
    print(hydro.rgns[k])
    tmp <- read.csv(paste0(accum_dir, TNs[i], hydro.rgns[k], '.csv'))
    tmp <- tmp[, c('COMID', 'UpCatCount', 'UpCatSum', 'UpCatAreaSqKm')]
    if(k == 1){
      outdf <- tmp
    }else{
      outdf <- rbind(outdf, tmp)
    }
  }
  outdf <- outdf[!duplicated(outdf), ]
  saveRDS(outdf, paste0(nmodel_dir, 'splitcat-metrics/',TNs[i],'UpCatMetrics.rds'))
}

#sc <- merge(sc, outdf, by='COMID', all.x=T)
#sc[is.na(sc)] <- 0
#sc$WtKgNWs <- sc$CatSum + sc$UpCatSum
#sc$WtWsCount <- sc$WtCatCount + sc$UpCatCount
#sc <- sc[, c('COMID','SITE_ID','WtlndKgNWs', 'WtlndCountWs')]
#write.csv(sc, paste0(nmodel_dir, 'splitcat-metrics/fullwatershed-splitcat-wetland-metrics.csv'), row.names = F)
```

## Combine mean number of downstream connections into a single long file

```{r, eval=F}
accum_dir <- "L:/Priv/CORFiles/Geospatial_Library_Projects/WetlandConnectivity/SpatialDataInputs/Wetlands_NLCD2011b/NitrogenModeling/Allocation_Accumulation/"
working_dir <- 'D:/WorkFolder/WetlandConnectivity/WetConnect_Apr2019/'
nmodel_dir <- paste0(working_dir,'nitrogen-modeling/')

hydro.rgns <- c("01","02","03S","03N","03W","04","05","06","07","08","09","10L","10U","11","12","13","14","15","16","17","18")

files <- c('CountDwnSlpWetlands_','CountDwnSlpWetlandsNR_')

for(i in 1:length(files)){
  for(k in 1:length(hydro.rgns)){
    print(hydro.rgns[k])
    tmp <- read.csv(paste0(accum_dir, files[i], hydro.rgns[k], '.csv'))
    tmp <- tmp[, c('COMID', 'WsCount', 'WsSum')]
    if(k == 1){
      out1 <- tmp
    }else{
      out1 <- rbind(out1, tmp)
    }
  }
  out1$DSlpWtWs <- out1$WsSum / out1$WsCount
  out1 <- subset(out1, select=c(COMID,DSlpWtWs))
  if(i == 1){
    outdf <- out1
  }else{
    names(out1) <- c('COMID','DSlpWtNrWs')
    outdf <- merge(outdf, out1, by='COMID')
  }
}

saveRDS(outdf, paste0(nmodel_dir, 'splitcat-metrics/CountDwnSlpWtWsMetrics.rds'))
```

## Combine StreamCat NLCD 2011 Upcat wetland areas for into a single long file

```{r, eval=F}
sc_dir <- 'L:/Priv/CORFiles/Geospatial_Library_Projects/StreamCat/Allocation_and_Accumulation/'

hydro.rgns <- c("01","02","03S","03N","03W","04","05","06","07","08","09","10L","10U","11","12","13","14","15","16","17","18")

for(i in 1:length(hydro.rgns)){
  print(hydro.rgns[i])
  tmp <- read.csv(paste0(sc_dir, 'nlcd2011_', hydro.rgns[i], '.csv'))
  tmp <- subset(tmp, select = c(COMID, UpCatVALUE_90, UpCatVALUE_95))
  if(i == 1){
    outdf <- tmp
  }else{
    outdf <- rbind(outdf, tmp)
  }
}

outdf <- outdf[!duplicated(outdf), ]
outdf$UpCatWtCount <- outdf$UpCatVALUE_90 + outdf$UpCatVALUE_95
outdf$UpCatWtCount <- outdf$UpCatWtCount / 900
outdf <- subset(outdf, select=c(COMID, UpCatWtCount))

saveRDS(outdf, paste0(nmodel_dir, 'splitcat-metrics/UpCatWtCount.rds'))
```

## Combine accumulated wetland areas by wetland type

```{r, eval=F}
accum_dir <- "L:/Priv/CORFiles/Geospatial_Library_Projects/WetlandConnectivity/SpatialDataInputs/Wetlands_NLCD2011b/NitrogenModeling/Allocation_Accumulation/"

Types <- c('Ripar','NRSur','NRSubPd','NRSubWd')
hydro.rgns <- c("01","02","03S","03N","03W","04","05","06","07","08","09","10L","10U","11","12","13","14","15","16","17","18")

for(i in 1:length(hydro.rgns)){
  print(hydro.rgns[i])
  for(k in 1:length(Types)){
    print(Types[k]) 
    tmp <- read.csv(paste0(accum_dir, 'WtAreasByType_', Types[k], '_', hydro.rgns[i], '.csv'))[, c('COMID','UpCatCount')]
    names(tmp)[2] <- paste0(Types[k], 'WtUpCount')
    if(k == 1){
      tmpdf <- tmp
    }else{
      tmpdf <- merge(tmpdf, tmp, by=)
    }
  }
  if(i == 1){
    outdf <- tmpdf
  }else{
    outdf <- rbind(outdf, tmpdf)
  }
}

saveRDS(outdf, paste0(nmodel_dir, 'splitcat-metrics/WetlandPxlUpCount.rds'))

```

# Prepare SplitCat metrics for combining with upstream StreamCat metrics

## Calculate N applied to NRSA SplitCats (entire area)

```{r, eval=F}
library(raster)

sc_dir <- 'L:/Priv/CORFiles/Geospatial_Library_Projects/StreamCat/NARS_SplitCat_Metrics/NRSA-2008-09/split_cat/splits/split_full/'
translation_dir <- 'L:/Priv/CORFiles/Geospatial_Library_Projects/StreamCat/NARS_SplitCat_Metrics/NRSA-2008-09/'
nraster_dir <- 'L:/Priv/CORFiles/Geospatial_Library_Projects/WetlandConnectivity/NitrogenModeling/LandscapeRasters/'
cmaq_dir <- 'L:/Priv/CORFiles/Geospatial_Library_Projects/StreamCat/LandscapeRasters/QAComplete/'
wet_dir <- 'D:/WorkFolder/WetlandConnectivity/WetConnect_Apr2019/Wetlands_NLCD2011b/AllWetlands/'
wetcat_dir <- 'D:/WorkFolder/WetlandConnectivity/WetConnect_Apr2019/Wetlands_NLCD2011b/WetlandCat/WetCats/'
nmodel_dir <- 'D:/WorkFolder/WetlandConnectivity/WetConnect_Apr2019/nitrogen-modeling/'
accum_dir <- 'L:/Priv/CORFiles/Geospatial_Library_Projects/StreamCat/Allocation_and_Accumulation/'

ndata <- read.csv(paste0(nmodel_dir, 'N.data.csv'))
translation <- read.csv(paste0(translation_dir, 'sites.csv'))[, c('SITE_ID','UNIQUE_ID')]
ndata <- merge(ndata, translation, by='SITE_ID')
cbnf <-  raster(paste0(nraster_dir, 'cbnf.tif'))
manure <- raster(paste0(nraster_dir, 'manure.tif'))
fert <- raster(paste0(nraster_dir, 'fert.tif'))
cmaq <- raster(paste0(cmaq_dir, 'TD_N.tif'))

tokg <- function(inras){
  count <- sum(!is.na(inras@data@values))
  sum <- cellStats(inras, 'sum')
  ha <- count * 900 * 0.0001 
  kg <- (sum / count) * ha
  return(kg)
}

sites <- as.character(ndata$UNIQUE_ID)
siteids <- as.character(ndata$SITE_ID)
for(i in 1:length(sites)){
  print(sites[i])
  sc <- paste0(sc_dir, sites[i], '.tif')
  if(file.exists(sc)){
    sc <- raster(sc)
    sc[!is.na(sc)] <- 1
    
    n1 <- crop(cbnf, extent(sc)) * sc
    n2 <- crop(manure, extent(sc)) * sc
    n3 <- crop(fert, extent(sc)) * sc
    n4 <- crop(cmaq, extent(sc)+c(-10000,10000,-10000,10000))
    n4 <- resample(n4, sc, method="ngb") * sc
    SUM <- tokg(n1) + tokg(n2) + tokg (n3) + tokg(n4)
    COUNT <- sum(!is.na(sc@data@values))
    if(i == 1){
      outdf <- data.frame(SITE_ID = siteids[i], UNIQUE_ID=sites[i], SUM=SUM, COUNT=COUNT)  
    }else{
      outdf <- rbind(outdf, 
                     data.frame(SITE_ID = siteids[i], UNIQUE_ID=sites[i], SUM=SUM, COUNT=COUNT))
    }
  }
}

tmp <- ndata[, c('SITE_ID','COMID')]
outdf <- merge(outdf, tmp, by='SITE_ID')
write.csv(outdf, paste0(nmodel_dir, 'splitcat-fullcatchment/full-splitcat-metrics.csv'), row.names = F)
```

## Combine full splitcat N (entire area not accounting for wetland basins) with StreamCat accumulations to create site-specific summaries

```{r, eval=F}
year='2011'

working_dir <- 'D:/WorkFolder/WetlandConnectivity/WetConnect_Apr2019/'
nmodel_dir <- paste0(working_dir,'nitrogen-modeling/')
accum_dir <- 'L:/Priv/CORFiles/Geospatial_Library_Projects/StreamCat/Allocation_and_Accumulation/'
nlcd_dir <- 'L:/Priv/CORFiles/Geospatial_Library_Projects/StreamCat/Allocation_and_Accumulation/'

hydro.rgns <- c("01","02","03S","03N","03W","04","05","06","07","08","09","10L","10U","11","12","13","14","15","16","17","18")

sc <- read.csv(paste0(nmodel_dir, 'splitcat-fullcatchment/full-splitcat-metrics.csv'))

n_types <- c('CBNF_', 'TD_N_','Fert_','Manure_')

for(k in 1:length(hydro.rgns)){
  print(hydro.rgns[k])
  
  nlcd <- read.csv(paste0(nlcd_dir, 'nlcd2011_', hydro.rgns[k], '.csv'))
  nlcd <- nlcd[, c(1, grep('UpCatVALUE', names(nlcd)))]
  nlcd[is.na(nlcd)] <- 0
  nlcd$UCC <- rowSums(nlcd[2:length(nlcd)]) / 900
  nlcd <- nlcd[, c('COMID','UCC')]
  
  for(i in 1:length(n_types)){
    #print(n_types[i])
    accum <- read.csv(paste0(accum_dir, n_types[i], hydro.rgns[k], '.csv'))[, c('COMID','UpCatCount','UpCatSum')]
    accum$UpCatHa <- (accum$UpCatCount * 900) * 0.0001  
    if(i == 1){
      outaccum <- subset(accum, select=COMID)
      outaccum$UpCatKg <- (accum$UpCatSum / accum$UpCatCount) * accum$UpCatHa
    }else{
      outaccum$UpCatKg <- outaccum$UpCatKg + ((accum$UpCatSum / accum$UpCatCount) * accum$UpCatHa)
    }
  }
  
  if(k == 1){
    outdf <- merge(nlcd, outaccum, by='COMID')
  }else{
    outdf <- rbind(outdf, merge(nlcd, outaccum, by='COMID'))
  }
}

saveRDS(outdf, paste0(nmodel_dir, 'splitcat-fullcatchment/full-upcat-metrics.rds'))

sc <- merge(sc, outdf, by='COMID', all.x=T)
sc$UpCatCount <- sc$UCC
sc <- subset(sc, select = -UCC)
sc[is.na(sc)] <- 0
sc$KgNWs <- sc$SUM + sc$UpCatKg
sc$CountWs <- sc$COUNT + sc$UpCatCount
sc <- sc[, c('COMID','SITE_ID','KgNWs', 'CountWs')]
write.csv(sc, paste0(nmodel_dir, 'splitcat-fullcatchment/fullwatershed-splitcat-metrics.csv'), row.names = F)
```

## Calculate N applied to **each wetland catchment** (by IDs) within NRSA SplitCats

TABLE INFO:
SITE_ID = NRSA SPLITCAT ID, WET_ID = WETLAND ID, WtCatCount = NUM. WETLAND CATCHMENT PIXELS
SUM = SUM TOTAL N (KG), CatCount = NUM. SPLITCAT PIXELS
rpu = NHDPLUS RASTER PROCESSING UNIT, COMID = NHDPLUS UNIQUE ID

* It is possible to have wetland areas that are larger than wetland catchment areas because of where NAs from full streams land and where the edge of splitcats occur. These have been verified to be correct.


```{r, eval=F}
library(raster)
library(dplyr)
# Define folders
sc_dir <- 'L:/Priv/CORFiles/Geospatial_Library_Projects/StreamCat/NARS_SplitCat_Metrics/NRSA-2008-09/split_cat/splits/split_full/'
translation_dir <- 'L:/Priv/CORFiles/Geospatial_Library_Projects/StreamCat/NARS_SplitCat_Metrics/NRSA-2008-09/'
nraster_dir <- 'L:/Priv/CORFiles/Geospatial_Library_Projects/WetlandConnectivity/NitrogenModeling/LandscapeRasters/'
cmaq_dir <- 'L:/Priv/CORFiles/Geospatial_Library_Projects/StreamCat/LandscapeRasters/QAComplete/'
nmodel_dir <- 'D:/WorkFolder/WetlandConnectivity/WetConnect_Apr2019/nitrogen-modeling/'
wetcat_dir <- 'D:/WorkFolder/WetlandConnectivity/WetConnect_Apr2019/Wetlands_NLCD2011b/WetlandCat/WetCats/'
wetland_dir <- 'D:/WorkFolder/WetlandConnectivity/WetConnect_Apr2019/Wetlands_NLCD2011b/AllWetlands_rpu/'
rpucomid <- read.csv('L:/Priv/CORFiles/Geospatial_Library_Projects/StreamCat/COMID_HydroRegion_RPU.csv')[c('COMID','RPU')]
ndata <- read.csv(paste0(nmodel_dir, 'N.data.csv'))
ndata <- merge(ndata, rpucomid, by='COMID')
translation <- read.csv(paste0(translation_dir, 'sites.csv'))[, c('SITE_ID','UNIQUE_ID')]
ndata <- merge(ndata, translation, by='SITE_ID')
# Read in rasters
cbnf <-  raster(paste0(nraster_dir, 'cbnf.tif'))
manure <- raster(paste0(nraster_dir, 'manure.tif'))
fert <- raster(paste0(nraster_dir, 'fert.tif'))
cmaq <- raster(paste0(cmaq_dir, 'TD_N.tif'))
#Create zonal stats function to get N to each wetland catchment in each splitcat
zonalstat <- function(inras, zonalras){
  inzone <- zonalras@data@values
  yes <- !is.na(inzone)
  if(sum(yes) != 0){
    ras <- inras@data@values[yes]
    inzone <- inzone[yes]
    tmp <- data.frame(ras=ras, inzone=inzone)
    tmp <- data.frame(tmp %>% group_by(inzone) %>% summarise(SUM=sum(ras), COUNT=n()))
    tmp$ha <- tmp$COUNT * 900 * 0.0001
    tmp$kg <- (tmp$SUM / tmp$COUNT) * tmp$ha
    tmp$SUM <- tmp$kg
    names(tmp)[1] <- 'WET_ID'
    #tmp$COUNT <- sum(yes)
    tmp <- tmp[ , c('WET_ID','COUNT','SUM')]
  }else{
    tmp <- data.frame(WET_ID=NA, SUM=0, COUNT=0)
  }
  return(tmp)
}

zonecount <- function(zonalras){
  inzone <- zonalras@data@values
  yes <- !is.na(inzone)
  if(sum(yes) != 0){
    inzone <- inzone[yes]
    tmp <- data.frame(inzone=inzone)
    tmp <- data.frame(tmp %>% group_by(inzone) %>% summarise(COUNT=n()))
    names(tmp)[1] <- 'WET_ID'
  }else{
    tmp <- data.frame(WET_ID=NA, COUNT=0)
  }
  return(tmp)
}

#Loop through RPUs to get wetland catchments
allsites <- as.character(ndata$SITE_ID)
unqids <- as.character(ndata$UNIQUE_ID)
rpus <- as.character(ndata$RPU)
unqrpus <- unique(rpus)
unqrpus <- unqrpus[order(unqrpus)]
for(k in 1:length(unqrpus)){
  print(unqrpus[k])
  wetcat <- raster(paste0(wetcat_dir, 'WetlandCat_', unqrpus[k], '.tif'))
  wetarea <- raster(paste0(wetland_dir, 'WetlandsRgnGrp_', unqrpus[k], '.tif'))
  sites <- allsites[rpus == unqrpus[k]]
  uniques <- unqids[rpus == unqrpus[k]]
  #Loop through splitcats and calc total kg of N
  for(i in 1:length(uniques)){
    print(uniques[i])
    sc <- paste0(sc_dir, uniques[i], '.tif')
    if(file.exists(sc)){
      sc <- raster(sc)
      #sc[!is.na(sc)] <- 1
      #read and crop rasters by splitcat
      wc <- crop(wetcat, extent(sc)) * sc
      if(!all(is.na(values(wc)))){
        wt <- crop(wetarea, extent(sc)) * sc
        n1 <- crop(cbnf, extent(sc)) * sc
        n2 <- crop(manure, extent(sc)) * sc
        n3 <- crop(fert, extent(sc)) * sc
        n4 <- crop(cmaq, extent(sc)+c(-10000,10000,-10000,10000))
        n4 <- resample(n4, sc, method="ngb") * sc
        #Cal zonal values for each wetland
        tmp <- zonalstat(n1,wc)
        tmp$SUM <- tmp$SUM + zonalstat(n2,wc)$SUM + zonalstat(n3,wc)$SUM + zonalstat(n4,wc)$SUM
        tmp$SITE_ID <- sites[i]
        tmp$UNIQUE_ID <- uniques[i]
        tmp$CatCount <- cellStats(sc, sum)
        tmp$rpu <- unqrpus[k]
        names(tmp)[2] <- 'WtCatCount'
        tmp2 <- zonecount(wt)
        names(tmp2)[2] <- 'WtCount'
        tmp <- merge(tmp, tmp2, by='WET_ID')
      }else{
        tmp <- data.frame(WET_ID=NA,  WtCatCount=0, SUM=0,
                          SITE_ID=sites[i], UNIQUE_ID=uniques[i], 
                          CatCount=cellStats(sc, sum), 
                          rpu=unqrpus[k], WtCount=NA)
      }
    }else{
      tmp <- data.frame(WET_ID=NA, WtCatCount=0, SUM=0, 
                        SITE_ID=sites[i], UNIQUE_ID=uniques[i], 
                        CatCount=cellStats(sc, sum), 
                        rpu=unqrpus[k], WtCount=NA)
    }
    if(i == 1){
      tmpdf <- tmp
    }else{
      tmpdf <- rbind(tmpdf, tmp)
    }
  }
  if(k == 1){
    outdf <- tmpdf
  }else{
    outdf <- rbind(outdf, tmpdf)
  }
}

# Pair with NHDPlus COMID
tmp <- ndata[, c('SITE_ID','COMID')]
outdf <- merge(outdf, tmp, by='SITE_ID')
write.csv(outdf, paste0(nmodel_dir, 'splitcat-wetlandbasin/splitcat-wetland-basin-metrics.csv'), row.names = F)
```

## Summarize wetland catchment N for each SITE_ID and by wetland type for each SITE_ID

```{r, eval=F}
library(dplyr)

year='2011'
rds_path <- paste0('L:/Priv/CORFiles/Geospatial_Library_Projects/WetlandConnectivity/SpatialDataInputs/Wetlands_NLCD',year,'b/FinalTables/')
table_path = paste0(rds_path, 'WetlandTables/')
nmodel_dir <- 'D:/WorkFolder/WetlandConnectivity/WetConnect_Apr2019/nitrogen-modeling/'

fullwetlands <- readRDS(paste0(rds_path, 'WetConnectMetrics_',year,'.rds'))
fullwetlands$Type_Full <- fullwetlands$Type
fullwetlands$Type <- ifelse(fullwetlands$Type=="Riparian", "Ripar", 
                            ifelse(fullwetlands$Type=="Overland", "NRSur",
                                   ifelse(fullwetlands$Type=='ShallowDeep' & fullwetlands$FreqClsPa=='VALUE_1',
                                          'NRSubPd', 'NRSubWd')))
fullwetlands$travel <- ifelse(fullwetlands$Type == 'NRSur', fullwetlands$MagOv, fullwetlands$MagSh)
fullwetlands$travel[fullwetlands$Type == 'Ripar'] <- 0
fullwetlands$travel <- fullwetlands$travel + 1
fullwetlands <- subset(fullwetlands, select = c(WetId,COMID,Type,travel,WetAreaSqKm))
fullwetlands$wetidcomid <- paste0(fullwetlands$WetId, '_', fullwetlands$COMID)

zonal <- read.csv(paste0(nmodel_dir, 'splitcat-wetlandbasin/splitcat-wetland-basin-metrics.csv'))
NAs <- zonal[is.na(zonal$WET_ID), ]
NAs <- subset(NAs, select=c(SITE_ID,SUM,WtCatCount,CatCount,WtCount,COMID))
names(NAs)[2] <- 'CatSum'
write.csv(NAs, paste0(nmodel_dir, 'splitcat-wetlandbasin/splitcat-wetland-basin-metrics--NAs.csv'), row.names=F)
zonal <- zonal[!is.na(zonal$WET_ID), ]
zonal$wetidcomid <- paste0(zonal$WET_ID, '_', zonal$COMID)
zonal <- subset(zonal, select = -COMID)
zonal <- merge(zonal, fullwetlands, by='wetidcomid')
zonal <- subset(zonal, select = -wetidcomid)
zonal$SUM[is.na(zonal$SUM)] <- 0
#SUM already as Kg
zonal$kg <- zonal$SUM
zonal$CatAreaSqKm <- (zonal$CatCount * 900) / 1e6
zonal$WetAreaSqKm <- (zonal$WtCount * 900) / 1e6
zonal$newsum <- zonal$kg / (zonal$WetAreaSqKm * 100)
zonal$newsum2 <- zonal$kg / (zonal$travel)
zonal$newsum3 <- zonal$kg / (zonal$WetAreaSqKm * 100) / (zonal$travel)

zonal0 <- zonal %>% group_by(SITE_ID) %>% summarize(CatSum=sum(kg),
                                                    WtCatCount=sum(WtCatCount),
                                                    CatCount=max(CatCount),
                                                    WtCount=sum(WtCount),
                                                    COMID=max(COMID))
zonal0 <- rbind(zonal0, NAs)

zonal1 <- zonal %>% group_by(SITE_ID) %>% summarize(CatSum=sum(newsum),
                                                    WtCatCount=sum(WtCatCount),
                                                    CatCount=max(CatCount),
                                                    WtCount=sum(WtCount),
                                                    COMID=max(COMID))
zonal1 <- rbind(zonal1, NAs)

zonal2 <- zonal %>% group_by(SITE_ID) %>% summarize(CatSum=sum(newsum2),
                                                    WtCatCount=sum(WtCatCount),
                                                    CatCount=max(CatCount),
                                                    WtCount=sum(WtCount),
                                                    COMID=max(COMID))
zonal2 <- rbind(zonal2, NAs)

zonal3 <- zonal %>% group_by(SITE_ID) %>% summarize(CatSum=sum(newsum3),
                                                    WtCatCount=sum(WtCatCount),
                                                    CatCount=max(CatCount),
                                                    WtCount=sum(WtCount),
                                                    COMID=max(COMID))
zonal3 <- rbind(zonal3, NAs)

write.csv(zonal0, file=paste0(nmodel_dir, 'splitcat-metrics/', 'TN_TotalKg_splitcat.csv'), row.names = F)
write.csv(zonal1, file=paste0(nmodel_dir, 'splitcat-metrics/', 'TN_ByWtArea_splitcat.csv'), row.names = F)
write.csv(zonal2, file=paste0(nmodel_dir, 'splitcat-metrics/', 'TN_ByTravelTime_splitcat.csv'), row.names = F)
write.csv(zonal3, file=paste0(nmodel_dir, 'splitcat-metrics/', 'TN_ByAreaTime_splitcat.csv'), row.names = F)


#Now summarize by wetland type
NAs$Type <- NA
NAs <- NAs[, c('Type','SITE_ID','CatSum','WtCatCount','CatCount','WtCount','COMID')]
NAs$Type <- as.character(NAs$Type)


zonal0 <- zonal %>% group_by(Type, SITE_ID) %>% summarize(CatSum=sum(kg),
                                                          WtCatCount=sum(WtCatCount),
                                                          CatCount=max(CatCount),
                                                          WtCount=sum(WtCount),
                                                          COMID=max(COMID))
zonal0 <- rbind(as.data.frame(zonal0), NAs)

zonal1 <- zonal %>% group_by(Type, SITE_ID) %>% summarize(CatSum=sum(newsum),
                                                          WtCatCount=sum(WtCatCount),
                                                          CatCount=max(CatCount),
                                                          WtCount=sum(WtCount),
                                                          COMID=max(COMID))
zonal1 <- rbind(as.data.frame(zonal1), NAs)

zonal2 <- zonal %>% group_by(Type, SITE_ID) %>% summarize(CatSum=sum(newsum2),
                                                          WtCatCount=sum(WtCatCount),
                                                          CatCount=max(CatCount),
                                                          WtCount=sum(WtCount),
                                                          COMID=max(COMID))
zonal2 <- rbind(as.data.frame(zonal2), NAs)

zonal3 <- zonal %>% group_by(Type, SITE_ID) %>% summarize(CatSum=sum(newsum3),
                                                          WtCatCount=sum(WtCatCount),
                                                          CatCount=max(CatCount),
                                                          WtCount=sum(WtCount),
                                                          COMID=max(COMID))
zonal3 <- rbind(as.data.frame(zonal3), NAs)

write.csv(zonal0, file=paste0(nmodel_dir, 'splitcat-metrics/', 'TN_TotalKg_ByType_splitcat.csv'), row.names = F)
write.csv(zonal1, file=paste0(nmodel_dir, 'splitcat-metrics/', 'TN_ByWtArea_ByType_splitcat.csv'), row.names = F)
write.csv(zonal2, file=paste0(nmodel_dir, 'splitcat-metrics/', 'TN_ByTravelTime_ByType_splitcat.csv'), row.names = F)
write.csv(zonal3, file=paste0(nmodel_dir, 'splitcat-metrics/', 'TN_ByAreaTime_ByType_splitcat.csv'), row.names = F)

```

# Combine wetland basin splitcat N (BY TYPE) with StreamCat wetland accumulations to create site-specific summaries

```{r, eval=F}
accum_dir <- "L:/Priv/CORFiles/Geospatial_Library_Projects/WetlandConnectivity/SpatialDataInputs/Wetlands_NLCD2011b/NitrogenModeling/Allocation_Accumulation/"
working_dir <- 'D:/WorkFolder/WetlandConnectivity/WetConnect_Apr2019/'
nmodel_dir <- paste0(working_dir,'nitrogen-modeling/')

hydro.rgns <- c("01","02","03S","03N","03W","04","05","06","07","08","09","10L","10U","11","12","13","14","15","16","17","18")

#sc <- read.csv(paste0(nmodel_dir, 'splitcat-metrics/', 'TN_TotalKg_splitcat.csv'))
Types <- c('Ripar','NRSur','NRSubPd','NRSubWd')

for(k in 1:length(hydro.rgns)){
  print(hydro.rgns[k])
  for(i in 1:length(Types)){
    print(Types[i])
    tmp <- read.csv(paste0(accum_dir, 'TN_TotalKg_', Types[i],  '_', hydro.rgns[k], '.csv'))
    if(i == 1){
      tmp <- tmp[, c('COMID', 'UpCatAreaSqKm', 'UpCatCount', 'UpCatSum')]
      names(tmp) <- c('COMID', 'UpCatAreaSqKm', paste0(Types[i], c('UpCount','UpSum')))
      out1 <- tmp
    }else{
      tmp <- tmp[, c('COMID', 'UpCatCount', 'UpCatSum')]
      names(tmp) <- c('COMID', paste0(Types[i], c('UpCount','UpSum')))
      out1 <- merge(out1, tmp, by='COMID')
    }
  }
  
  if(k == 1){
    outdf <- out1
  }else{
    outdf <- rbind(outdf, out1)
  }
}

outdf <- outdf[!duplicated(outdf), ]
saveRDS(outdf, paste0(nmodel_dir, 'splitcat-metrics/TN_TotalKg_UpCatMetrics_ByWetType.rds'))
```

# Combine full and wetland-filtered estimates of watershed N 

```{r, eval=F}
working_dir <- 'D:/WorkFolder/WetlandConnectivity/WetConnect_Apr2019/'
nmodel_dir <- paste0(working_dir,'nitrogen-modeling/')

outdf <- readRDS(paste0(nmodel_dir, 'splitcat-metrics/TN_TotalKg_UpCatMetrics_ByWetType.rds'))
dwnslp <- readRDS(paste0(nmodel_dir, 'splitcat-metrics/CountDwnSlpWtWsMetrics.rds'))
wtpxupcount <- readRDS(paste0(nmodel_dir, 'splitcat-metrics/WetlandPxlUpCount.rds'))

sc <- read.csv(paste0(nmodel_dir, 'splitcat-metrics/TN_TotalKg_ByType_splitcat.csv'))
scfull <- read.csv(paste0(nmodel_dir, 'splitcat-metrics/TN_TotalKg_splitcat.csv'))[, c('SITE_ID','CatCount')]

nout <- read.csv(paste0(nmodel_dir, 'N.data.csv'))
#nout <- nout[!(nout$SITE_ID %in% c('FW08AR218','FW08WI083')),] #Problem splitcat delineations

nout <- subset(nout, select=c(SITE_ID, COMID))

Types <- c('Ripar','NRSur','NRSubPd','NRSubWd')
#Take long tables of wetland type by COMID
for(i in 1:length(Types)){
  print(Types[i])
  tmp <- sc[sc$Type == Types[i], ]
  tmp <- tmp[, c('SITE_ID','CatSum','WtCatCount','WtCount')]
  nms <- paste0(Types[i], c('CatSum','WtCatCount','WtCount'))
  names(tmp) <- c('SITE_ID', nms)
  nout <- merge(nout, tmp, by='SITE_ID', all.x=T)
}

nout <- merge(nout, wtpxupcount, by='COMID')
nout <- merge(nout, outdf, by='COMID')
nout[is.na(nout)] <- 0
nout <- merge(nout, scfull, by='SITE_ID')
nout <- merge(nout, dwnslp, by='COMID')
nout$DSlpWtWs[is.na(nout$DSlpWtWs)] <- -1
nout$DSlpWtNrWs[is.na(nout$DSlpWtNrWs)] <- -1

write.csv(nout, paste0(nmodel_dir, 'splitcat-metrics/fullwatershed-splitcat-wetland-metrics-BYWETLAND-TYPE.csv'), row.names = F)

#------------------------------



# for(i in 1:length(Types)){
#   nout$tmp <- rowSums(nout[,grep(Types[i],names(nout))])
#   names(nout)[length(nout)] <- paste0(Types[i],'KgWs')
# }
# 
# nout <- nout[, c(1, 2, grep('KgWs',names(nout)))]
# write.csv(nout, paste0(nmodel_dir, 'splitcat-metrics/fullwatershed-splitcat-wetland-metrics-BYWETLAND-TYPE.csv'), row.names = F)
# 
# 
# wetn <- read.csv(paste0(nmodel_dir, 'splitcat-metrics/fullwatershed-splitcat-wetland-metrics-BYWETLAND-TYPE.csv'))
# fulln <- read.csv(paste0(nmodel_dir, 'splitcat-fullcatchment/fullwatershed-splitcat-metrics.csv'))
# fulln <- subset(fulln, select = -c(COMID,CountWs))
# inputn <- merge(wetn, fulln, by='SITE_ID')
# inputn$tmp <- rowSums(inputn[, grep('KgWs', names(inputn))])
# inputn$KgNNonWtWs <- inputn$KgNWs - inputn$tmp
# inputn <- subset(inputn, select=-tmp)
# 
# nout <- read.csv(paste0(nmodel_dir, 'N.data.csv'))
# nout <- nout[nout$SITE_ID != 'FW08AR218',]
# #nout[nout$SITE_ID == 'FW08LA035',]
# nout <- nout[, c('SITE_ID','TN','TP','DOC','q.ann','area')]
# nout$TNout <- (nout$TN * nout$q.ann * 60 * 60 * 24 * 365.24 * 1000) / 1e6
# #TN(mgN/L)*q.ann(m^3/s)*sec*min*hour*days*L/m^3 / mg/Kg = Kg/yr
# 
# ndata <- merge(nout, inputn, by='SITE_ID')
# ndata$lg_TNout <- log10(ndata$TNout+1)
# ndata$lg_KgNWs <- log10(ndata$KgNWs+1)
# ndata$lg_KgNNonWtWs <- log10(ndata$KgNNonWtWs+1)
# 
# ndata$lg_RiparKgWs <- log10(ndata$RiparKgWs+1)
# ndata$lg_NRSurKgWs <- log10(ndata$NRSurKgWs+1)
# ndata$lg_NRSubPdKgWs <- log10(ndata$NRSubPdKgWs+1)
# ndata$lg_NRSubWdKgWs <- log10(ndata$NRSubWdKgWs+1)
# 
# summary(lm(lg_TNout ~ lg_KgNWs, data=ndata))
# summary(lm(lg_TNout ~ lg_KgNNonWtWs+lg_RiparKgWs+lg_NRSurKgWs+lg_NRSubPdKgWs+lg_NRSubWdKgWs, data=ndata))
# 
# ndata$NRSubKgWs <- ndata$NRSubPdKgWs + ndata$NRSubWdKgWs
# ndata$lg_NRSubKgWs <- log10(ndata$NRSubKgWs+1)
# summary(lm(lg_TNout ~ lg_KgNNonWtWs+lg_RiparKgWs+lg_NRSurKgWs+lg_NRSubKgWs, data=ndata))
# 
# 
# ndata$NRKgWs <- ndata$NRSurKgWs + ndata$NRSubPdKgWs + ndata$NRSubWdKgWs
# ndata$lg_NRKgWs <- log10(ndata$NRKgWs+1)
# summary(lm(lg_TNout ~ lg_KgNNonWtWs+lg_RiparKgWs+lg_NRKgWs, data=ndata))
# 
# 
# ndata$lg_WtlndKgNWs <- log10(ndata$WtlndKgNWs+1)
# ndata$lg_TNconc <- log10(ndata$TN)
# 
# ndata$lg_KgNWsbyArea <- log10((ndata$KgNWs /ndata$area)+1)
# ndata$lg_KgNonbyArea <- log10((ndata$KgNNonWtWs / ndata$area)+1)
# ndata$lg_WtlndKgNWsbyArea <- log10((ndata$WtlndKgNWs / ndata$area)+1)
```

# Combine full and wetland-filtered N and model N out

```{r, eval=F}
# working_dir <- 'D:/WorkFolder/WetlandConnectivity/WetConnect_Apr2019/'
# nmodel_dir <- paste0(working_dir,'nitrogen-modeling/')
# 
# nout <- read.csv(paste0(nmodel_dir, 'N.data.csv'))
# nout <- nout[nout$SITE_ID != 'FW08AR218',]
# #nout[nout$SITE_ID == 'FW08LA035',]
# nout <- nout[, c('SITE_ID','TN','TP','DOC','q.ann','area')]
# nout$TNout <- (nout$TN * nout$q.ann * 60 * 60 * 24 * 365.24 * 1000) / 1e6
# #TN(mgN/L)*q.ann(m^3/s)*sec*min*hour*days*L/m^3 / mg/Kg = Kg/yr
# 
# wetn <- read.csv(paste0(nmodel_dir, 'splitcat-metrics/fullwatershed-splitcat-wetland-metrics.csv'))
# fulln <- read.csv(paste0(nmodel_dir, 'splitcat-fullcatchment/fullwatershed-splitcat-metrics.csv'))
# fulln <- subset(fulln, select = -COMID)
# 
# inputn <- merge(wetn, fulln, by='SITE_ID')
# inputn$KgNNonWtWs <- inputn$KgNWs - inputn$WtlndKgNWs
# ndata <- merge(nout, inputn, by='SITE_ID')
# ndata$lg_TNout <- log10(ndata$TNout+1)
# ndata$lg_KgNWs <- log10(ndata$KgNWs+1)
# ndata$lg_KgNNonWtWs <- log10(ndata$KgNNonWtWs+1)
# ndata$lg_WtlndKgNWs <- log10(ndata$WtlndKgNWs+1)
# ndata$lg_TNconc <- log10(ndata$TN)
# 
# ndata$lg_KgNWsbyArea <- log10((ndata$KgNWs /ndata$area)+1)
# ndata$lg_KgNonbyArea <- log10((ndata$KgNNonWtWs / ndata$area)+1)
# ndata$lg_WtlndKgNWsbyArea <- log10((ndata$WtlndKgNWs / ndata$area)+1)
# 
# # Models -------------------------------------------------------------
# 
# summary(lm(lg_TNout ~ lg_KgNWs, data=ndata))
# summary(lm(lg_TNout ~ lg_KgNNonWtWs+lg_WtlndKgNWs, data=ndata))
# 
# summary(lm(lg_TNconc ~ lg_KgNWsbyArea, data=ndata))
# summary(lm(lg_TNconc ~ lg_KgNonbyArea+lg_WtlndKgNWsbyArea, data=ndata))
# 
# plot(lg_KgNonbyArea~lg_WtlndKgNWsbyArea, data=ndata)
# 
# plot(lg_KgNNonWtWs~lg_WtlndKgNWs, data=ndata)
# summary(lm(lg_KgNNonWtWs~lg_WtlndKgNWs, data=ndata))
# 
# plot(lg_TNout ~ lg_KgNWs, data=ndata)
# plot(lg_TNout ~ lg_KgNNonWtWs, data=ndata)

```















# Add zonal N values and wetland areas to splitcats and calc catchment summaries

```{r, eval=F}
library(foreign)
library(dplyr)
year='2011'

nmodel_dir <- 'D:/WorkFolder/WetlandConnectivity/WetConnect_Apr2019/nitrogen-modeling/splitcat-wetlands/'
table_path = paste0('L:/Priv/CORFiles/Geospatial_Library_Projects/WetlandConnectivity/SpatialDataInputs/Wetlands_NLCD',year,'b/FinalTables/WetlandTables/')
zonal_path <- 'D:/WorkFolder/WetlandConnectivity/WetConnect_Apr2019/Wetlands_NLCD2011b/WetlandCat/Zonal/'
working_dir <- 'D:/WorkFolder/WetlandConnectivity/WetConnect_Apr2019/'
translation_dir <- 'D:/WorkFolder/WetlandConnectivity/WetConnect_Apr2019/nitrogen-modeling/'

translation <- read.csv(paste0(translation_dir, 'sites-comid-region.csv'))[, c('SITE_ID','COMID')]

hydroregions <- read.csv(paste0(working_dir, 'hydro-regions.csv'))
names(hydroregions) <- c('Region', 'RPU', 'Hydro')
rpus <- as.character(hydroregions$RPU)
vpus <- as.character(hydroregions$Hydro)

n_types <- c('cbnf_','CMAQ_','fert_','manure_')
outnames <- c('CBNF_','CMAQ_','Fert_','Manure_')

for(i in 1:length(n_types)){
  print(n_types[i])
  
  for(k in 1:length(rpus)){
    print(rpus[k])
    
    zonal <- read.dbf(paste0(zonal_path, n_types[i], rpus[k], '.dbf'))[, c('Value','COUNT','SUM')]
    splitcat <- read.csv(paste0(nmodel_dir, 'splitcat_wetid_assoc_', rpus[k], '.csv'))
    wetareas <- read.csv(paste0(table_path, 'BasinAreaSqKm_', rpus[k], '.csv'))[, c('WET_ID','COMID','WetlandAreaSqKm')]
    
    splitcat <- merge(splitcat, zonal, by.x='WET_ID', by.y='Value', all.x=T)
    splitcat <- merge(splitcat, wetareas, by.x='WET_ID', by.y='WET_ID', all.x=T)
    
    splitcat$ha <- (splitcat$COUNT * 900) * 0.0001  
    splitcat$kg <- (splitcat$SUM / splitcat$COUNT) * splitcat$ha
    splitcat$newsum <- splitcat$kg / (splitcat$WetlandAreaSqKm * 100)
    splitcat$newsum2 <- (splitcat$SUM / splitcat$COUNT) / (splitcat$WetlandAreaSqKm * 100)
    splitcat[is.na(splitcat$WET_ID), c('COUNT','SUM','WetlandAreaSqKm','ha','kg','newsum','newsum2')] <- 0
    
    missing <- as.character(splitcat$SITE_ID[is.na(splitcat$WET_ID)])
    #Fill in missing COMIDs
    splitcat$COMID[is.na(splitcat$WET_ID)] <-  translation$COMID[match(missing, translation$SITE_ID)]
    
    sc1 <- splitcat %>% group_by(SITE_ID) %>% summarize(SUM=sum(newsum), 
                                                        COUNT=sum(COUNT),
                                                        CatCount=max(SplitCatCount),
                                                        WetlandAreaSqKm = sum(WetlandAreaSqKm),
                                                        COMID=max(COMID))
    
    sc2 <- splitcat %>% group_by(SITE_ID) %>% summarize(SUM=sum(newsum2),
                                                        COUNT=sum(COUNT),
                                                        CatCount=max(SplitCatCount),
                                                        WetlandAreaSqKm = sum(WetlandAreaSqKm),
                                                        COMID=max(COMID))
    
    sc3 <- splitcat %>% group_by(SITE_ID) %>% summarize(SUM=sum(SUM), 
                                                        COUNT=sum(COUNT),
                                                        CatCount=max(SplitCatCount),
                                                        WetlandAreaSqKm = sum(WetlandAreaSqKm),
                                                        COMID=max(COMID))
    
    write.csv(sc1, file=paste0(working_dir, 'nitrogen-modeling/splitcat-allocation-accumulation/', outnames[i], 'wetlandarea1_', rpus[k], '.csv'), row.names = F) 
    write.csv(sc2, file=paste0(working_dir, 'nitrogen-modeling/splitcat-allocation-accumulation/', outnames[i], 'wetlandarea2_', rpus[k], '.csv'), row.names = F)
    write.csv(sc3, file=paste0(working_dir, 'nitrogen-modeling/splitcat-allocation-accumulation/', outnames[i], rpus[k], '.csv'), row.names = F)
  }
}
```

# Combine full splitcat N (non-wetland basins) with StreamCat accumulations to create site-specific summaries

```{r, eval=F}
library(foreign)
library(dplyr)
year='2011'

working_dir <- 'D:/WorkFolder/WetlandConnectivity/WetConnect_Apr2019/'
accum_dir <- 'L:/Priv/CORFiles/Geospatial_Library_Projects/WetlandConnectivity/SpatialDataInputs/Wetlands_NLCD2011b/NitrogenModeling/Allocation_Accumulation/'
nlcd_dir <- 'L:/Priv/CORFiles/Geospatial_Library_Projects/StreamCat/Allocation_and_Accumulation/'

hydroregions <- read.csv(paste0(working_dir, 'hydro-regions.csv'))
names(hydroregions) <- c('Region', 'RPU', 'Hydro')
rpus <- as.character(hydroregions$RPU)
vpus <- as.character(hydroregions$Hydro)

n_types <- c('CBNF_', 'CMAQ_','Fert_','Manure_')

for(i in 1:length(n_types)){
  print(n_types[i])
  
  for(k in 1:length(rpus)){
    print(rpus[k])
    
    sc <- read.csv(paste0(working_dir, 'nitrogen-modeling/splitcat-allocation-accumulation/', n_types[i], rpus[k], '.csv'))
    sc[sc$SITE_ID == 'FW08AR116',]
    
    
    
    
    
    
    
    
    accum <- read.csv(paste0(accum_dir, n_types[i], vpus[k], '.csv'))[, c('COMID','UpCatCount','UpCatSum')]
    nlcd <- read.csv(paste0(nlcd_dir, 'nlcd2011_', vpus[k], '.csv'))
    nlcd <- nlcd[, c(1, grep('UpCatVALUE', names(nlcd)))]
    nlcd[is.na(nlcd)] <- 0
    nlcd$UCC <- rowSums(nlcd[2:length(nlcd)]) / 900
    nlcd <- nlcd[, c('COMID','UCC')]
    
    sc <- merge(sc, accum, by='COMID', all.x=T)
    sc <- merge(sc, nlcd, by='COMID', all.x=T)
    sc$UpCatCount <- sc$UCC
    sc <- subset(sc, select = -UCC)
    sc[is.na(sc)] <- 0
    sc$tmp <- (sc$SUM + sc$UpCatSum) / (sc$CatCount + sc$UpCatCount)
    
    if(k == 1){
      outdf <- sc[, c('COMID','SITE_ID', 'tmp')]
    }else{
      outdf <- rbind(outdf, sc[, c('COMID','SITE_ID', 'tmp')])
    }
  }
  names(outdf)[length(outdf)] <- paste0(n_types[i], 'Wtlnd')
  write.csv(outdf, paste0(working_dir, 'nitrogen-modeling/splitcat-metrics/', n_types[i], 'splitcats.csv'), row.names = F)
}
```







