---
title: "National / Wetland Type Summaries"
author: "Ryan Hill"
date: "01/24/2020"
output: html_document
editor_options: 
  chunk_output_type: console
---

## National wetland summaries by Wetland Type

* sd = standard deviation
* da_to_wa = wetland drainage area : wetland area
* pathLen_m = flow distance (m) from wetland outlet to river/stream
* travel_days = flow travel time (days) 
* pctWetArea = % of CONUS comprised of wetlands (by wetland type)
* meanWetAreaSqKm = mean wetland area (km^2)
* pctWetIntercepted = % of CONUS intercepted by wetlands (by wetland type)
* AreaInterseptedSqKm = Area of CONUS intercepted by wetlands (by wetland type)

```{r, eval=T, warning=F, message=F}
library(foreign)
library(dplyr)
library(knitr)
year='2011'

n_zonal_path <- 'D:/WorkFolder/WetlandConnectivity/WetConnect_Oct2019/Wetlands_NLCD2011/NitrogenModeling/Allocation_Accumulation/'
rds_path <- 'D:/WorkFolder/WetlandConnectivity/WetConnect_Oct2019/Wetlands_NLCD2011/FinalTables/'
working_dir <- 'D:/WorkFolder/WetlandConnectivity/WetConnect_Oct2019/'
nmodel_dir <- paste0(working_dir,'nitrogen-modeling/')

wet <- readRDS(paste0(rds_path, 'WetConnectMetrics_',year,'--preliminary.rds'))
wet$Run[wet$Type == 'Ripar'] <- 0
wet$Drainarea_to_wetarea <- wet$DrainAreaSqKm / wet$WetAreaSqKm
wet$travel <- NA
wet$travel <- ifelse(wet$Type == 'NRSur' | wet$Type == 'NRSubPd', wet$MagOv, wet$MagSh)
wet$travel <- ifelse(wet$Type == 'Ripar', 0, wet$travel)

wetsummary <- wet %>% group_by(Type) %>% summarise(WetAreaSqKm=sum(WetAreaSqKm), NumWetlands=n(), 
                                                   median_da_to_wa=median(Drainarea_to_wetarea, na.rm = T), 
                                                   mean_da_to_wa=mean(Drainarea_to_wetarea, na.rm = T),
                                                   sd_da_to_wa=sd(Drainarea_to_wetarea, na.rm = T),
                                                   median_pathLen_m=median(Run, na.rm = T),
                                                   mean_pathLen_m=mean(Run, na.rm = T),
                                                   sd_pathLen_m=sd(Run, na.rm = T),
                                                   median_travel_days=median(travel, na.rm = T),
                                                   mean_travel_days=mean(travel, na.rm = T),
                                                   sd_travel_days=sd(travel, na.rm = T))
wetsummary[nrow(wetsummary) + 1, ] <- NA
wetsummary[nrow(wetsummary), 1] <- 'CONUS'
wetsummary[nrow(wetsummary), 2:3] <- colSums(wetsummary[ , 2:3], na.rm = T)
wetsummary$median_da_to_wa[nrow(wetsummary)] <- median(wet$Drainarea_to_wetarea, na.rm = T)
wetsummary$mean_da_to_wa[nrow(wetsummary)] <- mean(wet$Drainarea_to_wetarea, na.rm = T)
wetsummary$sd_da_to_wa[nrow(wetsummary)] <- sd(wet$Drainarea_to_wetarea, na.rm = T)

wetsummary$median_pathLen_m[nrow(wetsummary)] <- median(wet$Run, na.rm = T)
wetsummary$mean_pathLen_m[nrow(wetsummary)] <- mean(wet$Run, na.rm = T)
wetsummary$sd_pathLen_m[nrow(wetsummary)] <- sd(wet$Run, na.rm = T)

wetsummary$median_travel_days[nrow(wetsummary)] <- median(wet$travel, na.rm = T)
wetsummary$mean_travel_days[nrow(wetsummary)] <- mean(wet$travel, na.rm = T)
wetsummary$sd_travel_days[nrow(wetsummary)] <- sd(wet$travel, na.rm = T)


wetsummary$pctWetArea <- (wetsummary$WetAreaSqKm / 7663941.7) * 100
wetsummary$meanWetAreaSqKm <- wetsummary$WetAreaSqKm / wetsummary$NumWetlands

#Percent of US intercepted by wetlands
files <- list.files(paste0(n_zonal_path, 'DBF_stash/') , pattern = 'WtCatAreasByType_', full.names = T)

Types <- c('Ripar','NRSur','NRSubPd','NRSubWd')

for(k in 1:length(Types)){
  fls <- grep(Types[k], files, value = T)
  catcount <- 0
  for(i in 1:length(fls)){
    tmp <- read.dbf(fls[i])
    catcount <- catcount + sum(tmp$COUNT)
  }
  if(k == 1){
    outdf <- data.frame(Type=Types[k], CatCount=catcount)
  }else{
    outdf <- rbind(outdf, 
                   data.frame(Type=Types[k], CatCount=catcount))
  }
}

outdf$Type <- as.character(outdf$Type)
outdf[nrow(outdf) + 1, ] <- NA
outdf[nrow(outdf), 1] <- 'CONUS'
outdf[nrow(outdf), 2] <- sum(outdf$CatCount, na.rm = T)
outdf$AreaInterceptedSqKm <- (outdf$CatCount * 900) / 1e6
outdf$pctWetIntercepted <- (outdf$AreaInterceptedSqKm / 7663941.7) * 100
outdf <- subset(outdf, select=c(Type, pctWetIntercepted, AreaInterceptedSqKm))

wetsummary <- merge(wetsummary, outdf, by='Type', all.x=T)
wetsummary$Type[is.na(wetsummary$Type)] <- 'Unclassified'

rownames(wetsummary) <- wetsummary$Type
wetsummary[, 1] <- NULL

write.csv(wetsummary, 'L:/Public/rhill/bkup-nmodeling/figs-tables-summaries/summary_table-20200124.csv')

kable(wetsummary)


```






```{r, eval=F, warning=F, message=F, echo=F}
library(foreign)
library(dplyr)
library(knitr)
library(sf)
year='2011'

n_zonal_path <- 'L:/Priv/CORFiles/Geospatial_Library_Projects/WetlandConnectivity/SpatialDataInputs/Wetlands_NLCD2011b/NitrogenModeling/Allocation_Accumulation/'
sc_zonal_path <- 'L:/Priv/CORFiles/Geospatial_Library_Projects/StreamCat/Allocation_and_Accumulation/'
nhd_path <- 'D:/GISData/NHDPlusNationalData/NHDPlusV21_National_Seamless.gdb'
out_path <- 'D:/WorkFolder/WetlandConnectivity/Meetings/call-20190724/maps-20200124/'

n_types <- c('CBNF_','TD_N_','Fert_','Manure_')

for(k in 1:length(n_types)){
  print(n_types[k])
  files <- list.files(sc_zonal_path, n_types[k], full.names = T)
  files <- files[-grep('connectors', files)]
  if(length(-grep('Phos', files)) > 0) files <- files[-grep('Phos', files)]
  for(i in 1:length(files)){
    print(files[i])
    tmp <- read.csv(files[i])
    tmp$ha <- (tmp$CatCount * 900) * 0.0001  
    tmp$tmp <- (tmp$CatSum / tmp$CatCount) * tmp$ha
    tmp <- tmp[, c('COMID', 'tmp')]
    names(tmp) <- c('COMID', paste0(n_types[k],'kgN'))
    if(i == 1){
      tmp2 <- tmp
    }else{
      tmp2 <- rbind(tmp2, tmp)
    }
  }
  if(k == 1){
    totalN <- tmp2
  }else{
    totalN <- merge(totalN, tmp2, by='COMID')
  }
}

totalN$totalN <- rowSums(totalN[2:ncol(totalN)], na.rm = T)
totalN <- subset(totalN, select = c(COMID, totalN))

files <- list.files(paste0(n_zonal_path, 'DBF_stash/') , pattern = 'TN_TotalKg_', full.names = T)

Types <- c('Ripar','NRSur','NRSubPd','NRSubWd')
for(k in 1:length(Types)){
  print(Types[k])
  fls <- grep(Types[k], files, value = T)
  #catcount <- 0
  for(i in 1:length(fls)){
    tmp <- read.dbf(fls[i])
    tmp <- subset(tmp, select = c(VALUE, SUM))
    names(tmp) <- c('VALUE', paste0(Types[k], 'KgN'))
    if(i == 1){
      tmp2 <- tmp
    }else{
      tmp2 <- rbind(tmp2, tmp)
    }
  }
  if(k == 1){
    outdf <- tmp2
  }else{
    outdf <- merge(outdf, tmp2, by='VALUE', all = T)
  }
}

### outcats is gridcode and cats from catchments shapefiles in NHDPlus -- need to add code back in
#outcats <- st_read(nhd_path, 'Catchment')
#head(outcats)
#saveRDS(outcats, file = paste0(rds_path,'nhdplus-catchments.rds'))
outcats <- readRDS(paste0(rds_path,'nhdplus-catchments.rds'))

outdf <- merge(outcats, outdf, by.x='GRIDCODE', by.y='VALUE', all.x=T)
outdf <- outdf[outdf$GRIDCODE != 0, ]

totalN <- merge(totalN, outdf, by.x='COMID', by.y='FEATUREID', all.x = T)

totalN[is.na(totalN)] <- 0
totalN$geometry <- NULL

kgn <- grep('KgN', names(totalN), value=T)

totalN[paste0('pct', kgn)] <- (totalN[kgn] / totalN$totalN) * 100

totalN$test <- rowSums(totalN[kgn], na.rm = T)

#Wrote these files out for QA
#Found that in some cases, the catchment that is delineated for a wetland cat extend beyond the NHDPlus catchment due to flaws in DEM definitions of flow paths
#Total number where this happens is 25,107 - usually small catchments. Excluded from analysis.
qa_set <- totalN[totalN$test > totalN$totalN, ]
write.csv(qa_set, paste0(out_path, 'qa-check-pct-N-filtered.csv'), row.names = F)

tester <- totalN[totalN$totalN > totalN$test, ]
totalN2 <- subset(totalN2, select = -test)

write.csv(totalN2, paste0(out_path, 'pct_filtered.csv'), row.names = F)

tmp <- read.csv(paste0(out_path, 'pct_filtered.csv'))
pctN <- grep('pct', names(totalN), value=T)
tmp$pctNFiltered <- rowSums(tmp[pctN])
tmp$pctN_NoFilter <- 100 - tmp$pctNFiltered

write.csv(tmp, paste0(out_path, 'pct_filtered.csv'), row.names = F)

outsummary <- (colSums(totalN2[, c('totalN', kgn)]))

outpct <- (sum(outsummary[2:length(outsummary)]) / outsummary[1]) * 100
names(outpct) <- paste0('pct', names(outpct))

kable(outpct)

```


% of each catchment filtered

```{r, eval=F, warning=F, message=F, echo=F}
library(foreign)
library(dplyr)
sc_path <- 'L:/Priv/CORFiles/Geospatial_Library_Projects/StreamCat/FTP_Staging/StreamCat/HydroRegions/'
rds_path <- 'D:/WorkFolder/WetlandConnectivity/WetConnect_Oct2019/Wetlands_NLCD2011/FinalTables/'
cat_path <- 'D:/WorkFolder/WetlandConnectivity/WetConnect_Oct2019/Wetlands_NLCD2011/WetlandCat/WetCats/'
nhd_path <- 'D:/GISData/NHDPlusV21'

cat_files <- list.files(path=cat_path, pattern='.dbf')
cat_files <- cat_files[-grep('sr.lock', cat_files)]

for(i in 1:length(cat_files)){
  print(i)
  tmp <- read.dbf(paste0(cat_path, cat_files[i]))
  if(i == 1){
    wtcatcount <- tmp
  }else{
    wtcatcount <- rbind(wtcatcount, tmp)
  }
}

wtcatcount$WtCatAreaSqKm <- (wtcatcount$Count * 900) / 1e6
wtcatcount <- subset(wtcatcount, select = -Count)
names(wtcatcount) <- c('WetId','WtCatAreaSqKm')

wet <- readRDS(paste0(rds_path, 'WetConnectMetrics_',year,'--preliminary.rds'))
wet <- subset(wet, select = c(WetId, COMID, CatAreaSqKm))
wet <- merge(wet, wtcatcount, by='WetId', all.x=T)
wet$WtCatAreaSqKm[is.na(wet$WtCatAreaSqKm)] <- 0

tmp <- wet %>% group_by(COMID) %>% summarize(WtCatsArea = sum(WtCatAreaSqKm), CatAreaSqKm=max(CatAreaSqKm))
tmp <- data.frame(tmp)
#tmp <- tmp[tmp$WtCatsArea < tmp$CatAreaSqKm, ]
tmp$pctFilter <- (tmp$WtCatsArea / tmp$CatAreaSqKm) * 100
#25K cases where NHDPlus DEM has topography flow extending beyond NHDPlus catchments - set to 100%. 
tmp$pctFilter[tmp$pctFilter > 100] <- 100
tmp <- subset(tmp, select = -CatAreaSqKm)

sc_files <- list.files(sc_path, pattern = 'BFI')
for(i in 1:length(sc_files)){
  print(i)
  x <- read.csv(paste0(sc_path, sc_files[i]))
  x <- subset(x, select = c(COMID, CatAreaSqKm))
  if(i == 1){
    outsy <- x
  }else{
    outsy <- rbind(outsy, x)
  }
}

outsy <- merge(outsy, tmp, by='COMID', all.x=T)
outsy$pctFilter[is.na(outsy$pctFilter)] <- 0
write.csv(outsy, paste0(out_path, 'pct_area_filtered.csv'), row.names=F)
tmp <- subset(outsy, select=c(COMID, CatAreaSqKm))

tn <- read.csv(paste0(out_path, 'pct_filtered.csv'))
tn <- merge(tn, tmp, by='COMID')
tn$ha <- tn$CatAreaSqKm * 100
tn$TN_rate <- tn$totalN / tn$ha
write.csv(tn, paste0(out_path, 'pct_filtered2.csv'), row.names = F)

tn <- read.csv(paste0(out_path, 'pct_filtered2.csv'))
tn$TNrate_nofilter <- tn$TN_rate - (tn$TN_rate * (tn$pctNFiltered / 100))
tn$TNrate_filtered <- tn$TN_rate - (tn$TN_rate * (tn$pctN_NoFilter / 100))
write.csv(tn, paste0(out_path, 'pct_filtered2.csv'), row.names = F)

```

# Get TN applied to each wetland

```{r, eval=F, warning=F, message=F, echo=F}
library(foreign)
library(dplyr)
year='2011'
rds_path <- 'D:/WorkFolder/WetlandConnectivity/WetConnect_Oct2019/Wetlands_NLCD2011/FinalTables/'

zonal_path <- 'D:/WorkFolder/WetlandConnectivity/WetConnect_Oct2019/Wetlands_NLCD2011/WetlandCat/Zonal/'
working_dir <- 'D:/WorkFolder/WetlandConnectivity/WetConnect_Oct2019/'
hydroregions <- read.csv(paste0(working_dir, 'hydro-regions.csv'))
names(hydroregions) <- c('Region', 'RPU', 'Hydro')

rpus <- as.character(hydroregions$RPU)
n_types <- c('cbnf_','CMAQ_','fert_','manure_')

for(i in 1:length(rpus)){
  print(rpus[i])
  for(k in 1:length(n_types)){
    print(n_types[k])
    tmp <- read.dbf(paste0(zonal_path, n_types[k], rpus[i],'.dbf'))[, c('Value','SUM','COUNT')]
    #Convert total kg 
    tmp$ha <- (tmp$COUNT * 900) * 0.0001  
    tmp$tmp <- (tmp$SUM / tmp$COUNT) * tmp$ha
    tmp <- tmp[, c('Value', 'tmp')]
    names(tmp) <- c('Value', n_types[k])
    if(k == 1){
      outdf <- tmp
    }else{
      outdf <- merge(outdf, tmp, by='Value', all=T)
      #Sum columns of N kg
      #outdf$SUM <- rowSums(outdf[, 2:length(outdf)], na.rm = T)
      #Add dummy count column
      #outdf$COUNT <- 1
      #outdf <- outdf[, c('Value','COUNT','SUM')]
    }
  }
  if(i == 1){
    outdf2 <- outdf
  }else{
    outdf2 <- rbind(outdf2, outdf)
  }
  #write.dbf(outdf, file=paste0(zonal_path, 'TN_', rpus[i],'.dbf'))
}

names(outdf2) <- c('WetId','CBNF_KgN','TNDEP_KgN','Fert_KgN','Manure_KgN')

wet <- readRDS(paste0(rds_path, 'WetConnectMetrics_',year,'--preliminary.rds'))

wet <- merge(wet, outdf2, by='WetId', all.x = T)
wet <- subset(wet, select = -Type_Full)
names(wet)[4] <- 'Eco9'
#write.csv(wet, paste0(rds_path, 'WetlandConnectivity-ScienceHub-17092019.csv'), row.names = F)
wet$Magnitude <- wet$travel
wet <- subset(wet, select = -travel)

#wet <- read.csv(paste0(rds_path, 'WetlandConnectivity-ScienceHub-17092019.csv'))
wet <- subset(wet, select = -c(TypeRip, TypeOv, TypeSh, TypeShDp))

wet$Type <- ifelse(wet$Type == 'Ripar', 'Riparian',
                     ifelse(wet$Type == 'NRSur', 'NonRiparian-Surface',
                            ifelse(wet$Type == 'NRSubPd', 'NonRiparian-PD','NonRiparian-WD')))

write.csv(wet, paste0(rds_path, 'WetlandConnectivity-ScienceHub-20200128.csv'), row.names = F)

```

#TMP - code to get David Mushett data on wetlands

```{r, eval=F, warning=F, message=F, echo=F}

wd <- 'D:/WorkFolder/WetlandConnectivity/WetConnect_Apr2019/Mushet/'
wd2 <- 'L:/Public/rhill/Projects/WetlandConnectivity/ScienceHubData/'


#wet <- read.csv(paste0(wd2, 'WetConnectMetrics_',year,'--preliminary.rds'))

wetids <- read.dbf(paste0(wd, 'wetlands.tif.vat.dbf'))$Value

wet2 <- wet[wet$WetId %in% wetids, ]
#wet2 <- subset(wet2, select = -Type_Full)

#wet2$Magnitude <- ifelse(wet2$Type == 'NRSur' | wet2$Type == 'NRSubPd', wet2$MagOv, wet2$MagSh)

wet2$Type <- ifelse(wet2$Type == 'Ripar', 'Riparian',
                     ifelse(wet2$Type == 'NRSur', 'NonRiparian-Surface',
                            ifelse(wet2$Type == 'NRSubPd', 'NonRiparian-PD','NonRiparian-WD')))

# wet2 <- subset(wet2, select = c(WetId, PathID, COMID, WSA_9, WetRegion, State, CatAreaSqKm, DrainAreaSqKm, WetAreaSqKm, Type, MagOv,   
#                                 MagSh, Magnitude, Ppt2Yr24Hr, Slope, Manning, Run, PorosityMax, PermMin, PctWoody, TinerID, FreqClsPa))

write.csv(wet2, paste0(wd, 'WetlandMetrics-Kidder-Stutsman.csv'), row.names=F)

```





