
## Apply the same logic from StreamCat calculations to join with split metrics, grouping by SITE_ID instead of COMID.

### WetlandPoints were spatially joined to NRSA split-catchments using the script -> joinWetPts2NRSAsplitPolys.py
```{r, eval=F}
hm_path <- paste0('L:/Priv/CORFiles/Geospatial_Library/Data',
                  '/Project/WetlandConnectivity/')
n_path <- paste0(hm_path,'NitrogenModeling/')
# csv output from python script <- joinWetPts2NRSAsplitPolys.py
join_tbl <- read.csv(paste0(n_path,'join_nrsa_wet.csv'))

year <- '2011'
# wetland data relating to every WetId
rds <- readRDS(paste0(hm_path,'SpatialDataInputs/',
                      'Wetlands_NLCD',year,'/FinalTables/',
                      'WetConnectMetrics_2011.rds'))
# inner join tables to groupby SITE_ID and summarize
# this isolates only the wetlands whose points lie w/in split-cats
wrk_tbl <- merge(join,rds,by='WetId')
# the "wrk_tbl" object will be used for processing, but write out to save
write.csv(wrk_tbl,
          file = paste0(n_path,'WetConnectMetrics_2011wSplitCats.csv'),
          row.names = FALSE)
```

### Dominant Wetland Connectivity Type
```{r, eval=F}
library(dplyr)
library(tidyr)

wrk_tbl <- read.csv(paste0(hm_path,
                           '/NitrogenModeling/WetConnectMetrics_2011wSplitCats.csv'),
                     header=TRUE,sep=",")

# aggregate results to NRSA SITE_ID
by_COMID <- in_table %>%
            group_by(SITE_ID, Type) %>%
            summarize(CatDomTypeArea=sum(WetAreaSqKm))

by_COMID = as.data.frame(by_COMID)
zonal <- by_COMID %>% spread(Type, CatDomTypeArea)
names(zonal)[2:6] <- c('CatWetMissing','CatWetOverland','CatWetRiparian',
                       'CatWetShallow','CatWetShallowDeep')
zonal[is.na(zonal)] <- 0
zonal$CatWetAreaSqKm <- rowSums(zonal[,2:6])
zonal <- zonal[c("SITE_ID","CatWetAreaSqKm","CatWetOverland","CatWetRiparian",
                 "CatWetShallow","CatWetShallowDeep","CatWetMissing")]
final <- merge(x=join_tbl[,c("SITE_ID","CAT_COMID")],y=zonal,
              by="SITE_ID",all.x=TRUE)
final[is.na(final)] <- 0
write.csv(final, 
          file=paste0(hm_path,'/NitrogenModeling/splitMetrics/WetlandType.csv'),
          row.names = FALSE)
```

### Dominant Wetland Connectivity Frequency
```{r, eval=F}
library(dplyr)
library(tidyr)

hm_path = paste0('L:/Priv/CORFiles/Geospatial_Library/Data',
                  '/Project/WetlandConnectivity/NitrogenModeling')
join_table <- read.csv(paste0(hm_path, '/NRSA_Results/CBNF.csv'),
                       header=TRUE,sep=",")[,c("SITE_ID","CAT_COMID")]
in_table <- read.csv(paste0(hm_path, '/WetConnectMetrics_2011wSplitCats.csv'),
                     header=TRUE,sep=",")

# Ascribe Scott's type's to frequency to get dominant frequency
in_table$freq <- ifelse(
                  in_table$Type=="Riparian" | in_table$FreqPa==1, 
                  "H",
                  ifelse(in_table$FreqPa==.5, 
                    "M", 
                    "L"))

# old method -- no longer used 
# in_table$freq <- ifelse(
#                   in_table$Type=="Riparian"|in_table$Type=="Overland",
#                   ifelse(
#                     in_table$FreqOv>=-500, 
#                     "H", 
#                     ifelse(
#                       in_table$FreqOv>=-1000, 
#                       "M", 
#                       "L")),
#                   ifelse(
#                     in_table$FreqSh=="VALUE_1", 
#                     "H", 
#                     ifelse(
#                       in_table$FreqSh=="VALUE_2", 
#                       "M", 
#                       "L")))

# aggregate results to NRSA SITE_ID
by_COMID <- in_table %>%
            group_by(SITE_ID, freq) %>%
            summarize(CatDomTypeArea = sum(WetAreaSqKm))

by_COMID = as.data.frame(by_COMID)
zonal <- by_COMID %>% spread(freq, CatDomTypeArea)
names(zonal)[2:5] <- c('CatHighFreq','CatLowFreq','CatMedFreq','CatMissing')
zonal[is.na(zonal)] <- 0
zonal$CatWetAreaSqKm <- rowSums(zonal[,2:5])
zonal <- zonal[c("SITE_ID","CatWetAreaSqKm","CatHighFreq","CatLowFreq","CatMedFreq","CatMissing")]
final <- merge(x=join_table,y=zonal,by="SITE_ID",all.x=TRUE)
final[is.na(final)] <- 0
write.csv(final,file=paste0(hm_path,'/splitMetrics/WetlandFreq.csv'),row.names=FALSE)
```

### Dominant Wetland Connectivity Magnitude
```{r, eval=F}
library(dplyr)
library(tidyr)

join_table <- read.csv(paste0(hm_path, '/NRSA_Results/CBNF.csv'),
                       header=TRUE,sep=",")[,c("SITE_ID","CAT_COMID")]
in_table <- read.csv(paste0(hm_path, '/WetConnectMetrics_2011wSplitCats.csv'),
                     header=TRUE,sep=",")

# Ascribe Scott's type's to frequency to get dominant frequency
in_table$mag <- ifelse(
                  in_table$Type=="Riparian", 
                  "VF",
                  ifelse(
                    in_table$Type=="Overland", 
                    ifelse(
                      in_table$MagOv<=24, 
                      "VF", 
                      ifelse(
                        in_table$MagOv/24<=14,
                        "FA",
                        "MO")),
                    ifelse(
                      in_table$MagSh<=1, 
                      "VF", 
                      ifelse(
                        in_table$MagSh<=14, 
                        "FA", 
                        ifelse(
                          in_table$MagSh/365.25<=1, 
                          "MO", 
                          ifelse(
                            in_table$MagSh/365.25<=10, 
                            "SL", 
                            "VS"))))))

# aggregate results to NRSA SITE_ID
by_COMID <- in_table %>%
            group_by(SITE_ID, mag) %>%
            summarize(CatDomTypeArea = sum(WetAreaSqKm))

by_COMID <- as.data.frame(by_COMID)
zonal <- by_COMID %>% spread(mag, CatDomTypeArea)
idx <- which(!is.na(match(names(zonal),"<NA>")))
names(zonal)[idx] <- "Missing"
zonal[is.na(zonal)] <- 0
names(zonal)[2:6] <- c('CatModerate','CatSlow',
                       'CatVeryFast','CatVerySlow','CatMissing')
zonal$CatWetAreaSqKm <- rowSums(zonal[,2:6])
zonal$CatFast <- 0
zonal <- zonal[c("SITE_ID","CatWetAreaSqKm","CatVerySlow","CatSlow",
                 "CatModerate","CatFast","CatVeryFast")]
final <- merge(x=join_table,y=zonal,by="SITE_ID",all.x=TRUE)
final[is.na(final)] <- 0
write.csv(final, 
          file=paste0(hm_path,'/splitMetrics/WetlandMag.csv'),
          row.names = FALSE)
```

### Average Wetland Connectivity Magnitude
This is a continuous variable, rather than categorical, using either magnitude of overland flow or magnitude of shallow flow depending on wetland type.  Note also that magnitude shallow flow is in days and magnitude overland flow is in hours - convert to same units (hours)
```{r, eval=F}
library(dplyr)
library(tidyr)

join_table <- read.csv(paste0(hm_path, '/NRSA_Results/CBNF.csv'),
                       header=TRUE,sep=",")[,c("SITE_ID","CAT_COMID")]
in_table <- read.csv(paste0(hm_path, '/WetConnectMetrics_2011wSplitCats.csv'),
                     header=TRUE,sep=",")

in_table$MagSh <- in_table$MagSh*24
in_table$mag_avg <- ifelse(
                      in_table$Type=="Riparian", 
                      0, 
                      ifelse(
                        in_table$Type=="Overland", 
                        in_table$MagOv, 
                        in_table$MagSh))

# aggregate results to NRSA SITE_ID
by_COMID <- in_table %>%
            group_by(SITE_ID) %>%
            summarize(CatWetAreaSqKm=sum(WetAreaSqKm),
                      CatAvgConMag=sum(mag_avg*DrainAreaSqKm)/sum(DrainAreaSqKm))

zonal <- as.data.frame(by_COMID)
final <- merge(x=join_table,y=zonal,by="SITE_ID",all.x=TRUE)
final[is.na(final)] <- 0
write.csv(final, 
          file = paste0(hm_path,'/splitMetrics/WetlandMagAvg.csv'),
          row.names=FALSE)
```

### Dominant Wetland Connectivity Disturbance / Impact
```{r, eval=F}
library(dplyr)
library(tidyr)

hm_path <- paste0('L:/Priv/CORFiles/Geospatial_Library/Data',
                  '/Project/WetlandConnectivity/NitrogenModeling')
join_table <- read.csv(paste0(hm_path, '/NRSA_Results/CBNF.csv'),
                       header=TRUE,sep=",")[,c("SITE_ID","CAT_COMID")]

in_table <- read.csv(paste0(hm_path, '/WetConnectMetrics_2011wSplitCats.csv'),
                     header=TRUE,sep=",")
# Ascribe Scott's type's to disturbance to get dominant disturbance
in_table$imp <- ifelse(
                  in_table$Type=="Riparian",
                  ifelse(
                    rowSums(in_table[c("ImpDrImperv","ImpDrAg")])==0,
                    "N",
                    ifelse(
                      in_table["ImpDrImperv"]<=5 & in_table["ImpDrAg"]<=5,
                      "L",
                      "H")),
                  ifelse(
                    rowSums(in_table[c("ImpPaAg","ImpPaLev","ImpPaCan")])==0,
                    "N",
                    ifelse(
                      in_table["ImpDrImperv"]<=5 &
                        in_table["ImpDrAg"]<=5 &
                        in_table["ImpPaAg"]<=5 &
                        in_table["ImpPaLev"]==0 &
                        in_table["ImpPaCan"]==0,
                      "L",
                      "H")))

# aggregate results to NRSA SITE_ID
by_COMID <- in_table %>%
  group_by(SITE_ID, imp) %>%
  summarize(CatDomTypeArea = sum(WetAreaSqKm))

by_COMID <- as.data.frame(by_COMID)
zonal <- by_COMID %>% spread(imp, CatDomTypeArea)
names(zonal)[5] <- "Missing"
zonal[is.na(zonal)] <- 0
names(zonal)[2:5] <- c('CatHigh','CatLow','CatNone','CatMissing')
zonal$CatWetAreaSqKm <- rowSums(zonal[,2:5])
zonal <- zonal[, !(colnames(zonal) %in% c("CatMissing"))]

final <- merge(x=join_table,y=zonal,by="SITE_ID",all.x=TRUE)
final[is.na(final)] <- 0
final <- final[,c(1,2,6,3,4,5)]
write.csv(final, 
          file=paste0(hm_path,'/splitMetrics/WetlandDist.csv'),
          row.names=FALSE)
```

### Sum nitrogen inputs for wetland drainage pixels
```{r, eval=F}
library(tidyr)
library(stringr)
library(purrr)
library(plyr)
library(foreign)
library(dplyr)

capwords <- function(s, strict = FALSE) {
  cap <- function(s) paste(toupper(substring(s, 1, 1)),
                {s <- substring(s, 2); if(strict) tolower(s) else s},
                           sep = "", collapse = " " )
  sapply(strsplit(s, split = " "), cap, USE.NAMES = !is.null(names(s)))
}

readDB <- function(file){
  df <- read.dbf(file, as.is=FALSE)
  names(df) <- toupper(names(df))
  return(df)
}


hm <- 'L:/Priv/CORFiles/Geospatial_Library/Data/Project/WetlandConnectivity'
table_path = paste0(hm, '/SpatialDataInputs/Wetlands_NLCD',year,'/WetlandCat/Zonal/')
variables <- list.files(table_path)
allwet <- readRDS(paste0(hm,'/SpatialDataInputs/Wetlands_NLCD',year,
                         '/FinalTables/WetConnectMetrics_',year,'.rds'))
fromto_path <- paste0(hm,'/SpatialDataInputs/Wetlands_NLCD',year,'/WetlandCat/FlowTables')
from_to <- list.files(fromto_path)
join_table <- read.csv(paste0(hm, '/NitrogenModeling/join_nrsa_wet.csv'),
                       header=TRUE,sep=",")
all_sites <- read.dbf(paste0(hm,'/NitrogenModeling/NRSA_Polys/NRSA_split_polys_0809.dbf'), as.is = FALSE)[c('SITE_ID','CAT_COMID')]
tables <- c('manure_', 'fert_', 'cbnf_', 'CMAQ_', 'PointN_') # 

for (nm in tables){
  print(nm)
  cur_list = variables[grep(nm,variables)]
  cur_list <- cur_list[!grepl('\\.xml$',cur_list) & ! grepl('\\.cpg$',cur_list)]
  result <- ldply(paste0(table_path,'/',cur_list), readDB)
  if (nm != 'PointN_') result <- result[!is.na(result$COUNT),]
  # Issue of NAs with CMAQ data
  names(result)[1] <- 'WetId'
  if (nm == 'PointN_') final = result
  if (nm != 'PointN_') final <- result[c('WetId','AREA','COUNT','SUM')] # keep AREA here
  final$State <- allwet$State[match(final$WetId, allwet$WetId)]
  final$COMID <- allwet$COMID[match(final$WetId, allwet$WetId)]
  if (nm != 'PointN_') {
    final$MEAN <- final$SUM / final$COUNT
    # names(final)[3] <- 'DrainAreaSqKm'  # we want split area here
    # final$DrainAreaSqKm <- final$DrainAreaSqKm * 1e-6
    final <- final[c('WetId','AREA','COUNT','SUM','State','COMID','MEAN')]    
    names(final)[2] <- 'DrainAreaSqKm'
    final$DrainAreaSqKm <- final$DrainAreaSqKm * 1e-6
  } else {
    final <- final[c('WetId','COMID','SUM')]
  }

  in_table <- merge(join_table, final, by='WetId', all.x=TRUE)
  
  # aggregate results to NRSA SITE_ID
  # by_COMID <- in_table %>%
  #             group_by(SITE_ID) %>%
  #             dplyr::summarize(CAT_COMID=unique(CAT_COMID), 
  #                              CatMean=sum((MEAN*DrainAreaSqKm)/DrainAreaSqKm), 
  #                              CatDrainAreaSqKm=sum(DrainAreaSqKm))

  
  if (nm != 'PointN_'){
    
          by_COMID <- in_table %>%
            group_by(SITE_ID) %>%
            dplyr::summarize(CatMean= sum((MEAN*DrainAreaSqKm) / sum(DrainAreaSqKm)),
                             CatDrainAreaSqKm = sum(DrainAreaSqKm),
                             CatLoad = CatMean * CatDrainAreaSqKm
                             )
  } else {
    
          by_COMID <- in_table %>%
            group_by(SITE_ID) %>%
            dplyr::summarize(CAT_COMID=unique(CAT_COMID),
                             CatSum= sum(SUM))
  }
  
  # !! need to remove the _ underscore in Load columns!!
  
  zonal = as.data.frame(by_COMID)
  nm <- capwords(nm)
  if (nm != 'PointN_')names(zonal)[2] <- paste0('Cat',str_replace(nm,"_",""))
  zonal <- merge(all_sites, zonal[c('SITE_ID','CatSum')], by='SITE_ID', all.x=TRUE)
  if (nm != 'PointN_'){names(zonal)[5] <- paste0('Cat', nm, 'Load')}
  zonal[is.na(zonal)] <- 0
  if (nm != 'PointN_'){zonal <- zonal[c(1,2, 4 ,3,5)]}
  if (nm == 'PointN_')names(zonal)[3] <- paste0('Cat',str_replace(nm,"_",""))
  fn <- str_replace(nm,"_","") # remove underscore from 'PointN_'
  out <- paste0(hm,'/NitrogenModeling/splitMetrics/WetDrain',fn,'.csv')
  write.csv(zonal, 
            file=out,
            row.names=FALSE)
  }
```
